### 2022-09-28 Final_Project_Work_HW2.Rmd
Add files via upload

---
title: "Final_Project_Work_HW2_JaJuArEm"
author: "Jacob Kresnicka"
date: "2022-09-21"
output: html_document
---

# library statements

```{r}
library(ISLR)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
library(stringr)
library(splitstackshape)
```

# read in data

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
View(imdb_top_1000)
```

# data cleaning

```{r}
imdb_clean <- imdb_top_1000 %>%
  select(-Poster_Link, -Certificate) %>%
  cSplit("Genre", sep = ",", direction = "wide")

runtime_clean <- imdb_top_1000$Runtime %>%
  str_replace(" min", "") %>%
  as.numeric()

imdb_clean$Runtime <- runtime_clean

```

# creation of cv folds
# model spec
# recipes & workflows
# fit & tune models

### 2022-09-29 Final_Project_Work_HW2.Rmd
Newest version 9/28/2022

@@
 # creation of cv folds
+
+```{r}
+data_cv10 <- vfold_cv(imdb_clean, v = 10)
+```
+
 # model spec
+
+```{r}
+lm_spec <-
+    linear_reg() %>% 
+    set_engine(engine = 'lm') %>% 
+    set_mode('regression')
+```
+
 # recipes & workflows
+
+```{r}
+full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
+    step_rm(Series_Title, Released_Year, Overview) %>% 
+    step_nzv(all_predictors()) %>% 
+    step_normalize(all_numeric_predictors()) %>% 
+    step_dummy(all_nominal_predictors())
+
+full_lm_wf <- workflow() %>%
+    add_recipe(full_rec) %>%
+    add_model(lm_spec)
+
+full_model <- fit(full_lm_wf, data = imdb_clean)
+
+full_model %>% tidy()
+```
+
 # fit & tune models
+
+```{r}
+
+```

### 2022-09-29 Final_Project_Work_HW2.Rmd
Test

@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview) %>% 
+    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues
     step_nzv(all_predictors()) %>% 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Test 2

--- 2022-09-29 Final_Project_Work_HW2.Rmd
@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview) %>% 
+    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe
     step_nzv(all_predictors()) %>% 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Move to Git

--- 2022-09-29 Final_Project_Work_HW2.Rmd
@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview) %>% 
+    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe now
     step_nzv(all_predictors()) %>% 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Test

@@
 library(splitstackshape)
+tidymodels_prefer()
 ```

### 2022-09-29 Final_Project_Work_HW2.Rmd
First push

@@
 imdb_clean$Runtime <- runtime_clean
-
 ```
@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe now
+    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe this will work
     step_nzv(all_predictors()) %>% 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Added answer to #3

@@
 ```
+
+3.
+Analyzing and predicting gross revenue of movies could have harmful effects on the performance of movies in box offices.
+For example, if we were to use our model to predict the success of a new movie, our model's prediction would affect people's decision making in whether to see the movie.
+This could affect the actual outcome of how movies perform at the box office.
+Our model's predictions could introduce bias into people's decisions of whether or not to see a movie.
+
+The main caution we want to keep in mind when communicating our work is that our model may be bias against new names in the movie industry.
+The model cannot determine a director, actor, or actresses' talent.
+It only bases its predictions off of how previous movies that individual was involved in previously performed.

### 2022-09-29 Final_Project_Work_HW2.Rmd
Fixed model, making it more simple for now

@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe this will work
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
     step_nzv(all_predictors()) %>% 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Did some editing.
Done through residuals code for final fit

--- 2022-09-29 Final_Project_Work_HW2.Rmd
@@
 imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
-View(imdb_top_1000)
+head(imdb_top_1000)
 ```
@@
 full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe this will work
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
     step_nzv(all_predictors()) %>% 
     step_normalize(all_numeric_predictors()) %>% 
-    step_dummy(all_nominal_predictors())
+    step_dummy(all_nominal_predictors()) %>%
+    step_naomit(Gross)
 
@@
 
+# LASSO
+
 ```{r}
 
+# Lasso Model Spec with tune
+lm_lasso_spec_tune <- 
+  linear_reg() %>%
+  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
+  set_engine(engine = 'glmnet') %>% #note we are using a different engine
+  set_mode('regression')
+
+# Recipe with standardization (!) --> just include all these always
+data_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>%
+    step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
+    step_novel(all_nominal_predictors()) %>% # important if you have rare categorical variables 
+    step_normalize(all_numeric_predictors()) %>%  # super important standardization step for LASSO
+    step_dummy(all_nominal_predictors()) %>%  # creates indicator variables for categorical variables
+    step_naomit(Gross)
+
+# Workflow (Recipe + Model)
+lasso_wf_tune <- workflow() %>% 
+  add_recipe(data_rec) %>%
+  add_model(lm_lasso_spec_tune)
+
+# Tune Model (trying a variety of values of Lambda penalty)
+penalty_grid <- grid_regular(
+  penalty(range = c(-1, 8)),
+  levels = 60)
+
+tune_res <- tune_grid( # new function for tuning parameters
+  lasso_wf_tune, # workflow
+  resamples = data_cv10, # cv folds
+  metrics = metric_set(rmse, mae),
+  grid = penalty_grid # penalty grid defined above
+)
+
+# Visualize Model Evaluation Metrics from Tuning
+autoplot(tune_res) + theme_classic()
+
+# Summarize Model Evaluation Metrics (CV)
+collect_metrics(tune_res) %>%
+  filter(.metric == 'rmse') %>% # or choose mae
+  select(penalty, rmse = mean)
+
+best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+
+# Fit Final Model
+final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
+
+final_fit <- fit(final_wf, data = imdb_clean)
+
+tidy(final_fit)
 ```
+
+```{r}
+best_penalty <- select_best(tune_res, metric = 'mae') # choose penalty value based on lowest cv mae
+best_penalty
+
+# Use this if worried about overfitting
+best_se_penalty <- select_by_one_std_err(tune_res, metric = 'mae', desc(penalty)) # choose largest penalty value within 1 se of the lowest cv mae
+best_se_penalty
+```
+
+```{r}
+final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
+final_wf_se <- finalize_workflow(lasso_wf_tune, best_se_penalty) # incorporates penalty value to workflow
+
+final_fit <- fit(final_wf, data = imdb_clean)
+final_fit_se <- fit(final_wf_se, data = imdb_clean)
+
+tidy(final_fit)
+tidy(final_fit_se)
+```
+
+```{r}
+final_fit_se %>% tidy() %>% filter(estimate != 0)
+```
+
+```{r}
+lasso_mod_out <- final_fit_se %>%
+    predict(new_data = imdb_clean) %>%
+    bind_cols(imdb_clean) %>%
+    mutate(resid = Gross - .pred)
+
+ggplot(lasso_mod_out, aes(x = .pred, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = Runtime, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = IMDB_Rating, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = No_of_Votes, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+```
+
+2.
 

### 2022-09-29 Final_Project_Work_HW2.Rmd
Draft of HW2

@@
 ---
-title: "Final_Project_Work_HW2_JaJuArEm"
-author: "Jacob Kresnicka"
-date: "2022-09-21"
-output: html_document
+title: 'STAT 253 Final Project'
+author: "Jacob, Julian, Aristo, and Emily"
+date: "September 30, 2022"
+output: 
+  html_document:
+    df_print: paged
+    code_download: true
 ---
 
-# library statements
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
+```
+
+# Library Statements
 
@@
 
-# read in data
+# Read in Data
 
@@
 imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
-head(imdb_top_1000)
 ```
 
-# data cleaning
+# Data Cleaning
 
@@
   select(-Poster_Link, -Certificate) %>%
-  cSplit("Genre", sep = ",", direction = "wide")
+  cSplit("Genre", sep = ",", direction = "wide") %>%
+  mutate(Gross = log(Gross))
 
@@
 
-# creation of cv folds
+# Creation of CV Folds
 
@@
 
-# model spec
+# Model Spec for Linear Regression Model
 
@@
 
-# recipes & workflows
+# Recipes and Workflows
 
@@
 
-# fit & tune models
-
-# LASSO
+# LASSO - Fit and Tune Models
 
@@
 penalty_grid <- grid_regular(
-  penalty(range = c(-1, 8)),
-  levels = 60)
+  penalty(range = c(-3, 1)),
+  levels = 30)
 
@@
 autoplot(tune_res) + theme_classic()
+```
+
+# Collect CV Metrics and Select Best Model
+
+```{r}
 
@@
 best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+```
+
+# Fit Final Model
+
+```{r}
 
@@
 ```{r}
-best_penalty <- select_best(tune_res, metric = 'mae') # choose penalty value based on lowest cv mae
-best_penalty
+# Final ("best") model predictors and coefficients
 
-# Use this if worried about overfitting
-best_se_penalty <- select_by_one_std_err(tune_res, metric = 'mae', desc(penalty)) # choose largest penalty value within 1 se of the lowest cv mae
-best_se_penalty
+final_fit %>% tidy() %>% filter(estimate != 0)
 ```
 
-```{r}
-final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
-final_wf_se <- finalize_workflow(lasso_wf_tune, best_se_penalty) # incorporates penalty value to workflow
-
-final_fit <- fit(final_wf, data = imdb_clean)
-final_fit_se <- fit(final_wf_se, data = imdb_clean)
-
-tidy(final_fit)
-tidy(final_fit_se)
-```
+# Visualize Residuals
 
 ```{r}
-final_fit_se %>% tidy() %>% filter(estimate != 0)
-```
 
-```{r}
-lasso_mod_out <- final_fit_se %>%
+# Visualize Residuals
+lasso_mod_out <- final_fit %>%
     predict(new_data = imdb_clean) %>%
@@
 
-2.
-
-3.
-Analyzing and predicting gross revenue of movies could have harmful effects on the performance of movies in box offices.
-For example, if we were to use our model to predict the success of a new movie, our model's prediction would affect people's decision making in whether to see the movie.
-This could affect the actual outcome of how movies perform at the box office.
-Our model's predictions could introduce bias into people's decisions of whether or not to see a movie.
+The overall goal of our linear regression model is to predict a movie's gross box office revenue based on a number of predictors.
+The goal of our initial investigation was to determine which subset of predictors are the most important for inclusion in our model.
+In order to determine the "best" linear regression model to achieve our analysis goals, we utilized the LASSO algorithm.
+The goal of LASSO is to decrease variance in our model by constraining the coefficient estimates and discouraging the inclusion of weakly informative predictors through the use of a tuning parameter.
+This improves the predictive accuracy of our model.
+We chose this algorithm over the best subset selection algorithm because LASSO is substantially more computationally efficient.
+Furthermore, since our main analysis goal is predictive accuracy, we decided against using forward stepwise or backwards stepwise selection because these algorithms do not guarantee the best overall model.
+A model using a smaller subset of variables may have increased interpretability, but this would come at the expense of predictive accuracy.
 
@@
 It only bases its predictions off of how previous movies that individual was involved in previously performed.
+Furthermore, the inclusion of the number of votes predictor in our model raises further concerns of potential bias.
+Our initial evaluation of the residual vs.
+predictor plot revealed a textbook case of heteroscedasticity.
+Performing a log transformation on our outcome variable, gross revenue, improved this issue.
+However, there is still a slight pattern noticeable in the residual vs.
+predictor plot.
+Analysis of the residual vs.
+quantitative predictor plots reveals the number of votes predictor as the likely source of this error.
+The caution to keep in mind with the inclusion of this predictor is the idea of participation bias.
+In further investigations, we intend to evaluate whether to "override" the LASSO results and exclude the number of votes predictor from the model if we determine that it is introducing bias into our model.
+
+It is also important to consider any harms that may come from our analyses.
+Analyzing and predicting gross revenue of movies can have harmful effects on the performance of movies in box offices.
+For example, if we use our model to predict the success of a new movie, our model's prediction may affect people's decision as to whether or not to see the movie.
+This could affect the actual outcome of how movies perform at the box office by introducing bias into people's decision regarding whether to see a newly released movie.

### 2022-10-12 Final_Project_Work_HW2.Rmd
HW3 work

@@
 imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
+head(imdb_top_1000)
 ```
@@
 This could affect the actual outcome of how movies perform at the box office by introducing bias into people's decision regarding whether to see a newly released movie.
+
+```{r}
+lm_spec_gam <-
+  linear_reg() %>%
+  set_engine(engine = 'lm') %>%
+  set_mode('regression')
+
+full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
+    step_nzv(all_predictors()) %>% 
+    step_normalize(all_numeric_predictors()) %>% 
+    step_dummy(all_nominal_predictors()) %>%
+    step_naomit(Gross)
+
+spline_rec <- full_rec %>%
+     step_ns(Runtime, deg_free = edf) %>% 
+     step_ns(IMDB_Rating, deg_free = edf) %>%
+     step_ns(No_of_Votes, deg_free = edf)
+
+movie_wf <- workflow() %>%
+    add_model(lm_spec) %>%
+    add_recipe(full_rec)
+
+spline_wf <- workflow() %>%
+    add_model(lm_spec) %>%
+    add_recipe(spline_rec)
+
+fit_resamples(
+    movie_wf,
+    resamples = data_cv8, # cv folds
+    metrics = metric_set(mae,rmse,rsq)                     
+) %>% collect_metrics()
+```

### 2022-10-12 Final_Project_Work_HW2.Rmd
Work

@@
 ```{r}
+gam_spec <- 
+  gen_additive_mod() %>%
+  set_engine(engine = 'mgcv') %>%
+  set_mode('regression')
+
+gam_mod <- fit(gam_spec,
+    Gross ~ s(Runtime) + IMDB_Rating + s(Meta_score) + s(No_of_Votes) + Genre_1,
+    data = imdb_clean 
+)
+
+```
+
+```{r}
+gam_mod %>% pluck('fit') %>% mgcv::gam.check() 
+```
+
+```{r}
+gam_mod %>% pluck('fit') %>% plot()
+```
+
+```{r}
 lm_spec_gam <-
@@
 spline_rec <- full_rec %>%
-     step_ns(Runtime, deg_free = edf) %>% 
-     step_ns(IMDB_Rating, deg_free = edf) %>%
-     step_ns(No_of_Votes, deg_free = edf)
+     step_ns(Runtime, deg_free = 2) %>% 
+    step_ns(Meta_score, deg_free = 2) %>%
+     step_ns(No_of_Votes, deg_free = 6)
 
@@
     movie_wf,
-    resamples = data_cv8, # cv folds
+    resamples = data_cv10, # cv folds
     metrics = metric_set(mae,rmse,rsq)                     

### 2022-10-13 Final_Project_Work_HW2.Rmd
More for HW3

@@
 
+# Update your models to use natural splines for some of the quantitative predictors to account for non-linearity (these are GAMs).
+
 ```{r}
+# Build the GAM
+
 gam_spec <- 
@@
 ```{r}
+# Diagnostics: Check to see if the number of knots is large enough (if p-value is low, increase number of knots)
+
 gam_mod %>% pluck('fit') %>% mgcv::gam.check() 
@@
 ```{r}
+# Visualize: Look at the estimated non-linear functions
+
 gam_mod %>% pluck('fit') %>% plot()
@@
 ```{r}
+# Use the edf (round to integer) from above to create a recipe by adding step_ns() for the variables you want model with a non-linear relationship and do CV.
+Compare this model to one without any splines.
+
 lm_spec_gam <-
@@
   set_mode('regression')
+
+# data_cv10 <- imdb_clean %>% 
+#     filter(No_of_Votes < 1500000 & IMDB_Rating < 9) %>% # remove outliers
+#     vfold_cv(v = 10)
+
+data_cv10 <- vfold_cv(imdb_clean, v = 10)
 
@@
 ) %>% collect_metrics()
+
+# This code chunk has an error, but I'm not sure why
+
+# fit_resamples(
+#     spline_wf,
+#     resamples = data_cv10, # cv folds
+#     metrics = metric_set(mae,rmse,rsq)                     
+# ) %>% collect_metrics()
 ```
+
+# Compare insights from variable importance analyses here and the corresponding results from the Investigation
+
+```{r}
+# Lasso Model Spec with tune
+gam_lasso_spec_tune <- 
+  linear_reg() %>%
+  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
+  set_engine(engine = 'glmnet') %>% #note we are using a different engine
+  set_mode('regression')
+
+# Recipe with standardization (!) --> just include all these always
+data_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>%
+    step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
+    step_novel(all_nominal_predictors()) %>% # important if you have rare categorical variables 
+    step_normalize(all_numeric_predictors()) %>%  # super important standardization step for LASSO
+    step_dummy(all_nominal_predictors()) %>%  # creates indicator variables for categorical variables
+    step_naomit(Gross)
+
+# Workflow (Recipe + Model)
+lasso_wf_tune <- workflow() %>% 
+  add_recipe(data_rec) %>%
+  add_model(gam_lasso_spec_tune)
+
+# Tune Model (trying a variety of values of Lambda penalty)
+penalty_grid <- grid_regular(
+  penalty(range = c(-3, 1)),
+  levels = 30)
+
+tune_res <- tune_grid( # new function for tuning parameters
+  lasso_wf_tune, # workflow
+  resamples = data_cv10, # cv folds
+  metrics = metric_set(rmse, mae),
+  grid = penalty_grid # penalty grid defined above
+)
+
+# Visualize Model Evaluation Metrics from Tuning
+autoplot(tune_res) + theme_classic()
+```
+
+# Collect CV Metrics and Select Best Model
+
+```{r}
+
+# Summarize Model Evaluation Metrics (CV)
+collect_metrics(tune_res) %>%
+  filter(.metric == 'rmse') %>% # or choose mae
+  select(penalty, rmse = mean)
+
+best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+```
+
+# Fit Final Model
+
+```{r}
+
+# Fit Final Model
+final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
+
+final_fit <- fit(final_wf, data = imdb_clean)
+
+tidy(final_fit)
+```
+
+```{r}
+# Final ("best") model predictors and coefficients
+
+final_fit %>% tidy() %>% filter(estimate != 0)
+```
+
+# Visualize Residuals
+
+```{r}
+
+# Visualize Residuals
+lasso_mod_out <- final_fit %>%
+    predict(new_data = imdb_clean) %>%
+    bind_cols(imdb_clean) %>%
+    mutate(resid = Gross - .pred)
+
+ggplot(lasso_mod_out, aes(x = .pred, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = Runtime, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = IMDB_Rating, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = No_of_Votes, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+```
+
+# Compare model performance between your GAM models that the models that assuming linearity.
+
+# Summarize investigations
+
+Decide on an overall best model based on your investigations so far. To do this, make clear your analysis goals. Predictive accuracy? Interpretability? A combination of both?

### 2022-10-16 Final_Project_Work_HW2.Rmd
HW3 edits

@@
 library(splitstackshape)
+library(tidymodels)
+library(lubridate)
+library(rpart.plot)
+library(cluster)
+library(forcats)
 tidymodels_prefer()
@@
 
+full_modelcv <- fit_resamples(full_lm_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))
+
 full_model %>% tidy()
@@
 # Summarize Model Evaluation Metrics (CV)
-collect_metrics(tune_res) %>%
+lasso_mod <- collect_metrics(tune_res) %>%
   filter(.metric == 'rmse') %>% # or choose mae
@@
 best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+
+lasso_mod
 ```
@@
 final_fit <- fit(final_wf, data = imdb_clean)
+
+lasso_fit <- fit_resamples(final_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))
 
@@
 ```{r}
+gam_mod %>% pluck('fit') %>% summary() 
+```
+
+```{r}
 # Visualize: Look at the estimated non-linear functions
@@
 gam_mod %>% pluck('fit') %>% plot()
+```
+
+```{r}
+spline_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
+    step_rm(Series_Title, Released_Year, Overview,
+            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
+    step_nzv(all_predictors()) %>% 
+    step_normalize(all_numeric_predictors()) %>% 
+    step_dummy(all_nominal_predictors()) %>%
+    step_naomit(Gross) %>%
+    step_ns(Runtime, deg_free = 2) %>%
+    step_ns(No_of_Votes, deg_free = 6)
+
+spline_rec %>% prep(imdb_clean) %>% juice()
 ```
@@
 
-# data_cv10 <- imdb_clean %>% 
-#     filter(No_of_Votes < 1500000 & IMDB_Rating < 9) %>% # remove outliers
-#     vfold_cv(v = 10)
-
-data_cv10 <- vfold_cv(imdb_clean, v = 10)
-
-full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview,
-            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
-    step_nzv(all_predictors()) %>% 
-    step_normalize(all_numeric_predictors()) %>% 
-    step_dummy(all_nominal_predictors()) %>%
-    step_naomit(Gross)
-
-spline_rec <- full_rec %>%
-     step_ns(Runtime, deg_free = 2) %>% 
-    step_ns(Meta_score, deg_free = 2) %>%
-     step_ns(No_of_Votes, deg_free = 6)
-
-movie_wf <- workflow() %>%
-    add_model(lm_spec) %>%
-    add_recipe(full_rec)
-
 spline_wf <- workflow() %>%
@@
 
-fit_resamples(
-    movie_wf,
+cv_output <- fit_resamples( 
+  spline_wf, # workflow
   resamples = data_cv10, # cv folds
   metrics = metric_set(mae,rmse,rsq)
-) %>% collect_metrics()
+)
 
-# This code chunk has an error, but I'm not sure why
+cv_output %>% collect_metrics()
 
-# fit_resamples(
-#     spline_wf,
-#     resamples = data_cv10, # cv folds
-#     metrics = metric_set(mae,rmse,rsq)                     
-# ) %>% collect_metrics()
+```
+
+```{r}
+new_mod <- spline_wf %>%
+  fit(data = imdb_clean)
+
+new_mod %>%
+  tidy()
+
+new_mod %>% 
+  tidy() %>% 
+  arrange(desc(abs(statistic)))
+
+new_modcv <- fit_resamples(spline_wf, resamples = data_cv10, metrics = metric_set(mae, rmse, rsq))
 ```
@@
 # Workflow (Recipe + Model)
-lasso_wf_tune <- workflow() %>% 
+lasso_wf_tune1 <- workflow() %>% 
   add_recipe(data_rec) %>%
@@
 
-tune_res <- tune_grid( # new function for tuning parameters
-  lasso_wf_tune, # workflow
+tune_res1 <- tune_grid( # new function for tuning parameters
+  lasso_wf_tune1, # workflow
   resamples = data_cv10, # cv folds
@@
 # Visualize Model Evaluation Metrics from Tuning
-autoplot(tune_res) + theme_classic()
+autoplot(tune_res1) + theme_classic()
 ```
@@
 
-best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+best_penalty1 <- select_best(tune_res1, metric = 'rmse') # choose penalty value based on lowest mae or rmse
 ```
@@
 # Fit Final Model
-final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
+final_wf1 <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow
 
-final_fit <- fit(final_wf, data = imdb_clean)
+final_fit1 <- fit(final_wf1, data = imdb_clean)
 
-tidy(final_fit)
+tidy(final_fit1)
 ```
@@
 
-final_fit %>% tidy() %>% filter(estimate != 0)
+final_fit1 %>% tidy() %>% filter(estimate != 0)
 ```
@@
 # Visualize Residuals
-lasso_mod_out <- final_fit %>%
+lasso_mod_out1 <- new_mod %>%
     predict(new_data = imdb_clean) %>%
@@
 
-ggplot(lasso_mod_out, aes(x = .pred, y = resid)) +
+ggplot(lasso_mod_out1, aes(x = .pred, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out, aes(x = Runtime, y = resid)) +
+ggplot(lasso_mod_out1, aes(x = Runtime, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out, aes(x = IMDB_Rating, y = resid)) +
+ggplot(lasso_mod_out1, aes(x = IMDB_Rating, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out, aes(x = No_of_Votes, y = resid)) +
+ggplot(lasso_mod_out1, aes(x = No_of_Votes, y = resid)) +
     geom_point() +
@@
 
+```{r}
+full_modelcv %>% collect_metrics() #OLS
+```
+
+```{r}
+lasso_fit %>% collect_metrics() #LASSO
+```
+
+```{r}
+new_modcv %>% collect_metrics() #GAM
+```
+
 # Summarize investigations
@@
 Decide on an overall best model based on your investigations so far. To do this, make clear your analysis goals. Predictive accuracy? Interpretability? A combination of both?
+
+We want a combination of both, our spline model has the lowest RMSE but could be difficult to interpret.
+We need more visualization and analysis before we move forward.
+However we are confident in moving forward.
+
+# Societal Impact
+
+Being that the data here is about movies, the harm that could come from our analysis would be minimal. 
+Representation of different races, genders, abilities, etc.
+is an issue in Hollywood/the greater film industry, and it's likely that the harm our model/analysis produces is already in line with the issues that created and maintain this.
+This is because the data we have is on past movies that have come out of this system.
+This means that whatever has made a movie successful, whether it's due to certain actors or directors, or whatever — this is a standard that has already existed.
+If we see the movies that have done really well because the cast is predominantly white, well this has been going on a for a long time because Hollywood is racist.
+Our model can't account for that, but we are aware of it.

### 2022-10-17 Final_Project_Work_HW2.Rmd
HW 3 Final

@@
 author: "Jacob, Julian, Aristo, and Emily"
-date: "September 30, 2022"
+date: "October 17, 2022"
 output: 
@@
 imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
-head(imdb_top_1000)
 ```
@@
 
-# Update your models to use natural splines for some of the quantitative predictors to account for non-linearity (these are GAMs).
+# GAMs Using Splines
 
@@
 
-# Compare insights from variable importance analyses here and the corresponding results from the Investigation
+# Variable Importance for GAM
 
@@
 
-# Compare model performance between your GAM models that the models that assuming linearity.
+# Comparing Model Performance
 
@@
 
-# Summarize investigations
+# Summarize Investigations
 
-Decide on an overall best model based on your investigations so far. To do this, make clear your analysis goals. Predictive accuracy? Interpretability? A combination of both?
-
-We want a combination of both, our spline model has the lowest RMSE but could be difficult to interpret.
-We need more visualization and analysis before we move forward.
-However we are confident in moving forward.
+The goal of our investigations is to accurately predict a movie's gross box office revenue based on a number of predictors.
+We compared three different model types: ordinary linear regression (OLS) with all predictors, OLS using LASSO to select a subset of variables, and a GAM using splines to account for nonlinearity.
+The GAM model has the lowest RMSE but could be difficult to interpret.
+We are looking forward to continuing our investigations using Decision Trees which may offer a more easily interpreted method for modeling nonlinearity.
+Ideally, we would like an accurate model that is relatively easy to interpret.
 
@@
 
-Being that the data here is about movies, the harm that could come from our analysis would be minimal. 
+In addition to our earlier discussion of societal impacts that our model may have, we want to keep in mind the biases of the Hollywood movie industry.
 Representation of different races, genders, abilities, etc.
-is an issue in Hollywood/the greater film industry, and it's likely that the harm our model/analysis produces is already in line with the issues that created and maintain this.
-This is because the data we have is on past movies that have come out of this system.
-This means that whatever has made a movie successful, whether it's due to certain actors or directors, or whatever — this is a standard that has already existed.
-If we see the movies that have done really well because the cast is predominantly white, well this has been going on a for a long time because Hollywood is racist.
+is an issue in Hollywood/the greater film industry, and it is likely that the harm our model/analysis produces is already in line with the issues that created and maintain this.
+This is because the data we have is from past movies that came out of this system.
+This means that whatever made a movie successful, whether it's due to certain actors, directors, etc., is a standard that already existed.
+If we see the movies that have done really well have predominantly white casts, then it is likely a result of a longstanding issue of racism in the movie industry.
 Our model can't account for that, but we are aware of it.

### 2022-10-31 Final_Project_Classification_Models.Rmd
Started HW 4 Classification Models

---
title: 'STAT 253 Final Project - Classification Models'
author: "Jacob, Julian, Aristo, and Emily"
date: "October 31, 2022"
output: 
  html_document:
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

# Library Statements

```{r}
library(ISLR)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
library(stringr)
library(splitstackshape)
library(tidymodels)
library(lubridate)
library(rpart.plot)
library(cluster)
library(forcats)
tidymodels_prefer()
library(probably) #install.packages('probably')
library(vip)
```

# Read in Data

```{r}
library(readr)
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
```

# Data Cleaning

```{r}
imdb_clean <- imdb_top_1000 %>%
  select(-Poster_Link, -Certificate) %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = log(Gross))

runtime_clean <- imdb_top_1000$Runtime %>%
  str_replace(" min", "") %>%
  as.numeric()

imdb_clean$Runtime <- runtime_clean
```

# Logistic Regression

```{r}
# Logistic Regression Model Spec
logistic_spec <- logistic_reg() %>%
    set_engine('glm') %>%
    set_mode('classification')

# Recipe
logistic_rec <- recipe(___ ~ ., data = imdb_clean) %>%
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())

# Workflow (Recipe + Model)
log_wf <- workflow() %>% 
    add_recipe(logistic_rec) %>%
    add_model(logistic_spec)

# Fit Model to Training Data
log_fit <- fit(log_wf, data = imdb_clean)
```

### Examining the Logistic Regression Model

```{r}
# Print out Coefficients
log_fit %>% tidy()

# Get Exponentiated coefficients + CI
log_fit %>% tidy() %>%
  mutate(OR.conf.low = exp(estimate - 1.96*std.error), OR.conf.high = exp(estimate + 1.96*std.error)) %>% # do this first
  mutate(OR = exp(estimate))
```

### Making Prediction on Logistic Model

```{r}
# Make soft (probability) predictions
predict(log_fit, new_data = ___, type = "prob")

# Make hard (class) predictions (using a default 0.5 probability threshold)
predict(log_fit, new_data = ___, type = "class")
```

### Evaluating Logistic Model on Training Data

```{r}
# Soft predictions
logistic_output <-  data %>%
  bind_cols(predict(log_fit, new_data = data, type = 'prob'))

# Hard predictions (you pick threshold)
logistic_output <- logistic_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_REFLEVEL, levels(outcome), threshold = .8)) #Try changing threshold (.5, 0, 1, .2, .8)

# Visualize Soft Predictions
logistic_output %>%
  ggplot(aes(x = outcome, y = .pred_OUTCOME)) +
  geom_boxplot() + 
  geom_hline(yintercept = 0.5, color='red') +  # try changing threshold
  labs(y = 'Predicted Probability of Outcome', x = 'Observed Outcome') +
  theme_classic()
```

# Calculating Evaluation Metrics

```{r}
# Confusion Matrix
logistic_output %>%
  conf_mat(truth = outcome, estimate = .pred_class)

log_metrics <- metric_set(sens, yardstick::spec, accuracy) # these metrics are based on hard predictions

#sens: sensitivity = chance of correctly predicting second level, given second level (Yes)
#spec: specificity = chance of correctly predicting first level, given first level (No)
#accuracy: accuracy = chance of correctly predicting outcome

logistic_output %>% 
  log_metrics(estimate = .pred_class, truth = outcome, event_level = "second") # set second level of outcome as "success"
```

### ROC Curve

```{r}
logistic_roc <- logistic_output %>% 
    roc_curve(outcome, .pred_OUTCOME, event_level = "second") # set second level of outcome as "success"

autoplot(logistic_roc) + theme_classic()
```

### Evaluation Metrics Using CV

```{r}
# CV Fit Model
log_cv_fit <- fit_resamples(
    log_wf, 
    resamples = data_cv10,
    metrics = metric_set(sens, yardstick::spec, accuracy, roc_auc),
    control = control_resamples(save_pred = TRUE, event_level = 'second'))  # you need predictions for ROC calculations

collect_metrics(log_cv_fit) #default threshold is 0.5
```

# Logistic Model with LASSO

```{r}
set.seed(123)

# Make sure you set reference level (to the outcome you are NOT interested in)
spam <- spam %>%
  mutate(spam = relevel(factor(spam), ref='not_spam')) #set reference level

data_cv10 <- vfold_cv(spam, v = 10)

# Logistic LASSO Regression Model Spec
logistic_lasso_spec_tune <- logistic_reg() %>%
    set_engine('glmnet') %>%
    set_args(mixture = 1, penalty = tune()) %>%
    set_mode('classification')

# Recipe
logistic_rec <- recipe(_____, data = spam) %>%
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())

# Workflow (Recipe + Model)
log_lasso_wf <- workflow() %>% 
    add_recipe(logistic_rec) %>%
    add_model(logistic_lasso_spec_tune)

# Tune Model (trying a variety of values of Lambda penalty)
penalty_grid <- grid_regular(
  penalty(range = c(__,__)), #log10 transformed 
  levels = 100)

tune_output <- tune_grid( 
  log_lasso_wf, # workflow
  resamples = data_cv10, # cv folds
  metrics = metric_set(roc_auc,accuracy),
  control = control_resamples(save_pred = TRUE, event_level = 'second'),
  grid = penalty_grid # penalty grid defined above
)

# Visualize Model Evaluation Metrics from Tuning
autoplot(tune_output) + theme_classic()
```

### Inspecting the Model

```{r}
# Visualize Model Evaluation Metrics from Tuning
autoplot(tune_output) + theme_classic()
```

```{r}
# Select Penalty
best_se_penalty <- select_by_one_std_err(tune_output, metric = 'roc_auc', desc(penalty)) # choose penalty value based on the largest penalty within 1 se of the highest CV roc_auc
best_se_penalty

# Fit Final Model
final_fit_se <- finalize_workflow(log_lasso_wf, best_se_penalty) %>% # incorporates penalty value to workflow 
    fit(data = spam)

final_fit_se %>% tidy()
```

```{r}
# Comment on Variable Importance

glmnet_output <- final_fit_se %>% extract_fit_engine()

# Create a boolean matrix (predictors x lambdas) of variable exclusion
bool_predictor_exclude <- glmnet_output$beta==0

# Loop over each variable
var_imp <- sapply(seq_len(nrow(bool_predictor_exclude)), function(row) {
    this_coeff_path <- bool_predictor_exclude[row,]
    if(sum(this_coeff_path) == ncol(bool_predictor_exclude)){ return(0)}else{
    return(ncol(bool_predictor_exclude) - which.min(this_coeff_path) + 1)}
})

# Create a dataset of this information and sort
var_imp_data <- tibble(
    var_name = rownames(bool_predictor_exclude),
    var_imp = var_imp
)
var_imp_data %>% arrange(desc(var_imp))
```

# Evaluation Metrics

```{r}

# CV results for "best lambda"
tune_output %>%
    collect_metrics() %>%
    filter(penalty == best_se_penalty %>% pull(penalty))

# Count up number of spam and not_spam emails in the training data
spam %>%
    count(spam) # Name of the outcome variable goes inside count()

# Compute the NIR
```

### Final Model

```{r}
# Soft Predictions on Training Data
final_output <- final_fit_se %>% predict(new_data = spam, type='prob') %>% bind_cols(spam)
```

```{r}
# Use soft predictions
final_output %>%
    roc_curve(spam,.pred_spam,event_level = 'second') %>%
    autoplot()
```

```{r}
# thresholds in terms of reference level
threshold_output <- final_output %>%
    threshold_perf(truth = spam, estimate = .pred_not_spam, thresholds = seq(0,1,by=.01))

# J-index v. threshold for not_spam
threshold_output %>%
    filter(.metric == 'j_index') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'J-index', x = 'threshold') +
    theme_classic()

threshold_output %>%
    filter(.metric == 'j_index') %>%
    arrange(desc(.estimate))

# Distance v. threshold for not_spam

threshold_output %>%
    filter(.metric == 'distance') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'Distance', x = 'threshold') +
    theme_classic()

threshold_output %>%
    filter(.metric == 'distance') %>%
    arrange(.estimate)

log_metrics <- metric_set(accuracy,sens,yardstick::spec)

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_not_spam, levels(spam), threshold = ___ )) %>%
    log_metrics(truth = spam, estimate = .pred_class, event_level = 'second')
```

# Bagging and Random Forests

```{r}
# Model Specification
rf_spec <- rand_forest() %>%
  set_engine(engine = 'ranger') %>% 
  set_args(mtry = NULL, # size of random subset of variables; default is floor(sqrt(number of total predictors))
           trees = 1000, # Number of trees
           min_n = 2,
           probability = FALSE, # FALSE: get hard predictions (not needed for regression)
           importance = 'impurity') %>% # we'll come back to this at the end
  set_mode('classification') # change this for regression

# Recipe
data_rec <- recipe(class ~ ., data = land)

# Workflows
data_wf_mtry2 <- workflow() %>%
  add_model(rf_spec %>% set_args(mtry = 2)) %>%
  add_recipe(data_rec)

## Create workflows for mtry = 12, 74, and 147

data_wf_mtry12 <-

data_wf_mtry74 <-

data_wf_mtry147 <- 
```

```{r}
# Fit Models
set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
data_fit_mtry2 <- fit(data_wf_mtry2, data = land)

# Fit models for 12, 74, 147
set.seed(123) 
data_fit_mtry12 <-

set.seed(123)
data_fit_mtry74 <-

set.seed(123) 
data_fit_mtry147 <- 
```

```{r}
# Custom Function to get OOB predictions, true observed outcomes and add a user-provided model label
rf_OOB_output <- function(fit_model, model_label, truth){
    tibble(
          .pred_class = fit_model %>% extract_fit_engine() %>% pluck('predictions'), #OOB predictions
          class = truth,
          label = model_label
      )
}

#check out the function output
rf_OOB_output(data_fit_mtry2,2, land %>% pull(class))
```

```{r}
# Evaluate OOB Metrics

data_rf_OOB_output <- bind_rows(
    rf_OOB_output(data_fit_mtry2,2, land %>% pull(class)),
    rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)),
    rf_OOB_output(data_fit_mtry74,74, land %>% pull(class)),
    rf_OOB_output(data_fit_mtry147,147, land %>% pull(class))
)

data_rf_OOB_output %>% 
    group_by(label) %>%
    accuracy(truth = class, estimate = .pred_class)
```

### Evaluating the Forest

```{r}
rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)) %>%
    conf_mat(truth = class, estimate= .pred_class)
```

### Variable Importance

```{r}
# Impurity

model_output <-data_fit_mtry12 %>% 
    extract_fit_engine()

model_output %>% 
    vip(num_features = 30) + theme_classic() #based on impurity

model_output %>% vip::vi() %>% head()
model_output %>% vip::vi() %>% tail()
```

```{r}
# Permutation

model_output2 <- data_wf_mtry12 %>% 
  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
  fit(data = land) %>% 
    extract_fit_engine()

model_output2 %>% 
    vip(num_features = 30) + theme_classic()

model_output2 %>% vip::vi() %>% head()
model_output2 %>% vip::vi() %>% tail()
```

### 2022-11-01 Logistic_Regression_Model.Rmd
Started Logistic Regression Model

--- 2022-10-31 Final_Project_Classification_Models.Rmd
@@
 ```
-
-# Logistic Regression
-
-```{r}
-# Logistic Regression Model Spec
-logistic_spec <- logistic_reg() %>%
-    set_engine('glm') %>%
-    set_mode('classification')
-
-# Recipe
-logistic_rec <- recipe(___ ~ ., data = imdb_clean) %>%
-    step_normalize(all_numeric_predictors()) %>% 
-    step_dummy(all_nominal_predictors())
-
-# Workflow (Recipe + Model)
-log_wf <- workflow() %>% 
-    add_recipe(logistic_rec) %>%
-    add_model(logistic_spec)
-
-# Fit Model to Training Data
-log_fit <- fit(log_wf, data = imdb_clean)
-```
-
-### Examining the Logistic Regression Model
-
-```{r}
-# Print out Coefficients
-log_fit %>% tidy()
-
-# Get Exponentiated coefficients + CI
-log_fit %>% tidy() %>%
-  mutate(OR.conf.low = exp(estimate - 1.96*std.error), OR.conf.high = exp(estimate + 1.96*std.error)) %>% # do this first
-  mutate(OR = exp(estimate))
-```
-
-### Making Prediction on Logistic Model
-
-```{r}
-# Make soft (probability) predictions
-predict(log_fit, new_data = ___, type = "prob")
-
-# Make hard (class) predictions (using a default 0.5 probability threshold)
-predict(log_fit, new_data = ___, type = "class")
-```
-
-### Evaluating Logistic Model on Training Data
-
-```{r}
-# Soft predictions
-logistic_output <-  data %>%
-  bind_cols(predict(log_fit, new_data = data, type = 'prob'))
-
-# Hard predictions (you pick threshold)
-logistic_output <- logistic_output %>%
-  mutate(.pred_class = make_two_class_pred(.pred_REFLEVEL, levels(outcome), threshold = .8)) #Try changing threshold (.5, 0, 1, .2, .8)
-
-# Visualize Soft Predictions
-logistic_output %>%
-  ggplot(aes(x = outcome, y = .pred_OUTCOME)) +
-  geom_boxplot() + 
-  geom_hline(yintercept = 0.5, color='red') +  # try changing threshold
-  labs(y = 'Predicted Probability of Outcome', x = 'Observed Outcome') +
-  theme_classic()
-```
-
-# Calculating Evaluation Metrics
-
-```{r}
-# Confusion Matrix
-logistic_output %>%
-  conf_mat(truth = outcome, estimate = .pred_class)
-
-log_metrics <- metric_set(sens, yardstick::spec, accuracy) # these metrics are based on hard predictions
-
-#sens: sensitivity = chance of correctly predicting second level, given second level (Yes)
-#spec: specificity = chance of correctly predicting first level, given first level (No)
-#accuracy: accuracy = chance of correctly predicting outcome
-
-logistic_output %>% 
-  log_metrics(estimate = .pred_class, truth = outcome, event_level = "second") # set second level of outcome as "success"
-```
-
-### ROC Curve
-
-```{r}
-logistic_roc <- logistic_output %>% 
-    roc_curve(outcome, .pred_OUTCOME, event_level = "second") # set second level of outcome as "success"
-
-autoplot(logistic_roc) + theme_classic()
-```
-
-### Evaluation Metrics Using CV
-
-```{r}
-# CV Fit Model
-log_cv_fit <- fit_resamples(
-    log_wf, 
-    resamples = data_cv10,
-    metrics = metric_set(sens, yardstick::spec, accuracy, roc_auc),
-    control = control_resamples(save_pred = TRUE, event_level = 'second'))  # you need predictions for ROC calculations
-
-collect_metrics(log_cv_fit) #default threshold is 0.5
-```
-
 # Logistic Model with LASSO
@@
 ```
-
-# Bagging and Random Forests
-
-```{r}
-# Model Specification
-rf_spec <- rand_forest() %>%
-  set_engine(engine = 'ranger') %>% 
-  set_args(mtry = NULL, # size of random subset of variables; default is floor(sqrt(number of total predictors))
-           trees = 1000, # Number of trees
-           min_n = 2,
-           probability = FALSE, # FALSE: get hard predictions (not needed for regression)
-           importance = 'impurity') %>% # we'll come back to this at the end
-  set_mode('classification') # change this for regression
-
-# Recipe
-data_rec <- recipe(class ~ ., data = land)
-
-# Workflows
-data_wf_mtry2 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 2)) %>%
-  add_recipe(data_rec)
-
-## Create workflows for mtry = 12, 74, and 147
-
-data_wf_mtry12 <-
-
-data_wf_mtry74 <-
-
-data_wf_mtry147 <- 
-```
-
-```{r}
-# Fit Models
-set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
-data_fit_mtry2 <- fit(data_wf_mtry2, data = land)
-
-# Fit models for 12, 74, 147
-set.seed(123) 
-data_fit_mtry12 <-
-
-set.seed(123)
-data_fit_mtry74 <-
-
-set.seed(123) 
-data_fit_mtry147 <- 
-```
-
-```{r}
-# Custom Function to get OOB predictions, true observed outcomes and add a user-provided model label
-rf_OOB_output <- function(fit_model, model_label, truth){
-    tibble(
-          .pred_class = fit_model %>% extract_fit_engine() %>% pluck('predictions'), #OOB predictions
-          class = truth,
-          label = model_label
-      )
-}
-
-#check out the function output
-rf_OOB_output(data_fit_mtry2,2, land %>% pull(class))
-```
-
-```{r}
-# Evaluate OOB Metrics
-
-data_rf_OOB_output <- bind_rows(
-    rf_OOB_output(data_fit_mtry2,2, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry74,74, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry147,147, land %>% pull(class))
-)
-
-data_rf_OOB_output %>% 
-    group_by(label) %>%
-    accuracy(truth = class, estimate = .pred_class)
-```
-
-### Evaluating the Forest
-
-```{r}
-rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)) %>%
-    conf_mat(truth = class, estimate= .pred_class)
-```
-
-### Variable Importance
-
-```{r}
-# Impurity
-
-model_output <-data_fit_mtry12 %>% 
-    extract_fit_engine()
-
-model_output %>% 
-    vip(num_features = 30) + theme_classic() #based on impurity
-
-model_output %>% vip::vi() %>% head()
-model_output %>% vip::vi() %>% tail()
-```
-
-```{r}
-# Permutation
-
-model_output2 <- data_wf_mtry12 %>% 
-  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
-  fit(data = land) %>% 
-    extract_fit_engine()
-
-model_output2 %>% 
-    vip(num_features = 30) + theme_classic()
-
-model_output2 %>% vip::vi() %>% head()
-model_output2 %>% vip::vi() %>% tail()
-```

### 2022-11-02 Final_Project_Classification_Models.Rmd
Tentative Forest Model

@@
 ```{r}
-library(readr)
-imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
+imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000_updated.csv")
 ```
@@
 imdb_clean <- imdb_top_1000 %>%
-  select(-Poster_Link, -Certificate) %>%
   cSplit("Genre", sep = ",", direction = "wide") %>%
-  mutate(Gross = log(Gross))
+  mutate(Gross = log(revenue))
 
@@
 imdb_clean$Runtime <- runtime_clean
-```
 
-# Logistic Regression
+imdb_clean_class <- imdb_clean %>%
+  mutate(success_ratio = revenue/budget) %>%
+  mutate(flop = as.factor(ifelse(success_ratio > 1, 'FALSE', 'TRUE'))) %>%
+  filter(!is.na(flop))
 
-```{r}
-# Logistic Regression Model Spec
-logistic_spec <- logistic_reg() %>%
-    set_engine('glm') %>%
-    set_mode('classification')
-
-# Recipe
-logistic_rec <- recipe(___ ~ ., data = imdb_clean) %>%
-    step_normalize(all_numeric_predictors()) %>% 
-    step_dummy(all_nominal_predictors())
-
-# Workflow (Recipe + Model)
-log_wf <- workflow() %>% 
-    add_recipe(logistic_rec) %>%
-    add_model(logistic_spec)
-
-# Fit Model to Training Data
-log_fit <- fit(log_wf, data = imdb_clean)
-```
-
-### Examining the Logistic Regression Model
-
-```{r}
-# Print out Coefficients
-log_fit %>% tidy()
-
-# Get Exponentiated coefficients + CI
-log_fit %>% tidy() %>%
-  mutate(OR.conf.low = exp(estimate - 1.96*std.error), OR.conf.high = exp(estimate + 1.96*std.error)) %>% # do this first
-  mutate(OR = exp(estimate))
-```
-
-### Making Prediction on Logistic Model
-
-```{r}
-# Make soft (probability) predictions
-predict(log_fit, new_data = ___, type = "prob")
-
-# Make hard (class) predictions (using a default 0.5 probability threshold)
-predict(log_fit, new_data = ___, type = "class")
-```
-
-### Evaluating Logistic Model on Training Data
-
-```{r}
-# Soft predictions
-logistic_output <-  data %>%
-  bind_cols(predict(log_fit, new_data = data, type = 'prob'))
-
-# Hard predictions (you pick threshold)
-logistic_output <- logistic_output %>%
-  mutate(.pred_class = make_two_class_pred(.pred_REFLEVEL, levels(outcome), threshold = .8)) #Try changing threshold (.5, 0, 1, .2, .8)
-
-# Visualize Soft Predictions
-logistic_output %>%
-  ggplot(aes(x = outcome, y = .pred_OUTCOME)) +
-  geom_boxplot() + 
-  geom_hline(yintercept = 0.5, color='red') +  # try changing threshold
-  labs(y = 'Predicted Probability of Outcome', x = 'Observed Outcome') +
-  theme_classic()
-```
-
-# Calculating Evaluation Metrics
-
-```{r}
-# Confusion Matrix
-logistic_output %>%
-  conf_mat(truth = outcome, estimate = .pred_class)
-
-log_metrics <- metric_set(sens, yardstick::spec, accuracy) # these metrics are based on hard predictions
-
-#sens: sensitivity = chance of correctly predicting second level, given second level (Yes)
-#spec: specificity = chance of correctly predicting first level, given first level (No)
-#accuracy: accuracy = chance of correctly predicting outcome
-
-logistic_output %>% 
-  log_metrics(estimate = .pred_class, truth = outcome, event_level = "second") # set second level of outcome as "success"
-```
-
-### ROC Curve
-
-```{r}
-logistic_roc <- logistic_output %>% 
-    roc_curve(outcome, .pred_OUTCOME, event_level = "second") # set second level of outcome as "success"
-
-autoplot(logistic_roc) + theme_classic()
-```
-
-### Evaluation Metrics Using CV
-
-```{r}
-# CV Fit Model
-log_cv_fit <- fit_resamples(
-    log_wf, 
-    resamples = data_cv10,
-    metrics = metric_set(sens, yardstick::spec, accuracy, roc_auc),
-    control = control_resamples(save_pred = TRUE, event_level = 'second'))  # you need predictions for ROC calculations
-
-collect_metrics(log_cv_fit) #default threshold is 0.5
-```
-
-# Logistic Model with LASSO
-
-```{r}
-set.seed(123)
-
-# Make sure you set reference level (to the outcome you are NOT interested in)
-spam <- spam %>%
-  mutate(spam = relevel(factor(spam), ref='not_spam')) #set reference level
-
-data_cv10 <- vfold_cv(spam, v = 10)
-
-# Logistic LASSO Regression Model Spec
-logistic_lasso_spec_tune <- logistic_reg() %>%
-    set_engine('glmnet') %>%
-    set_args(mixture = 1, penalty = tune()) %>%
-    set_mode('classification')
-
-# Recipe
-logistic_rec <- recipe(_____, data = spam) %>%
-    step_normalize(all_numeric_predictors()) %>% 
-    step_dummy(all_nominal_predictors())
-
-# Workflow (Recipe + Model)
-log_lasso_wf <- workflow() %>% 
-    add_recipe(logistic_rec) %>%
-    add_model(logistic_lasso_spec_tune)
-
-# Tune Model (trying a variety of values of Lambda penalty)
-penalty_grid <- grid_regular(
-  penalty(range = c(__,__)), #log10 transformed 
-  levels = 100)
-
-tune_output <- tune_grid( 
-  log_lasso_wf, # workflow
-  resamples = data_cv10, # cv folds
-  metrics = metric_set(roc_auc,accuracy),
-  control = control_resamples(save_pred = TRUE, event_level = 'second'),
-  grid = penalty_grid # penalty grid defined above
-)
-
-# Visualize Model Evaluation Metrics from Tuning
-autoplot(tune_output) + theme_classic()
-```
-
-### Inspecting the Model
-
-```{r}
-# Visualize Model Evaluation Metrics from Tuning
-autoplot(tune_output) + theme_classic()
-```
-
-```{r}
-# Select Penalty
-best_se_penalty <- select_by_one_std_err(tune_output, metric = 'roc_auc', desc(penalty)) # choose penalty value based on the largest penalty within 1 se of the highest CV roc_auc
-best_se_penalty
-
-# Fit Final Model
-final_fit_se <- finalize_workflow(log_lasso_wf, best_se_penalty) %>% # incorporates penalty value to workflow 
-    fit(data = spam)
-
-final_fit_se %>% tidy()
-```
-
-```{r}
-# Comment on Variable Importance
-
-glmnet_output <- final_fit_se %>% extract_fit_engine()
-
-# Create a boolean matrix (predictors x lambdas) of variable exclusion
-bool_predictor_exclude <- glmnet_output$beta==0
-
-# Loop over each variable
-var_imp <- sapply(seq_len(nrow(bool_predictor_exclude)), function(row) {
-    this_coeff_path <- bool_predictor_exclude[row,]
-    if(sum(this_coeff_path) == ncol(bool_predictor_exclude)){ return(0)}else{
-    return(ncol(bool_predictor_exclude) - which.min(this_coeff_path) + 1)}
-})
-
-# Create a dataset of this information and sort
-var_imp_data <- tibble(
-    var_name = rownames(bool_predictor_exclude),
-    var_imp = var_imp
-)
-var_imp_data %>% arrange(desc(var_imp))
-```
-
-# Evaluation Metrics
-
-```{r}
-
-# CV results for "best lambda"
-tune_output %>%
-    collect_metrics() %>%
-    filter(penalty == best_se_penalty %>% pull(penalty))
-
-# Count up number of spam and not_spam emails in the training data
-spam %>%
-    count(spam) # Name of the outcome variable goes inside count()
-
-# Compute the NIR
-```
-
-### Final Model
-
-```{r}
-# Soft Predictions on Training Data
-final_output <- final_fit_se %>% predict(new_data = spam, type='prob') %>% bind_cols(spam)
-```
-
-```{r}
-# Use soft predictions
-final_output %>%
-    roc_curve(spam,.pred_spam,event_level = 'second') %>%
-    autoplot()
-```
-
-```{r}
-# thresholds in terms of reference level
-threshold_output <- final_output %>%
-    threshold_perf(truth = spam, estimate = .pred_not_spam, thresholds = seq(0,1,by=.01))
-
-# J-index v. threshold for not_spam
-threshold_output %>%
-    filter(.metric == 'j_index') %>%
-    ggplot(aes(x = .threshold, y = .estimate)) +
-    geom_line() +
-    labs(y = 'J-index', x = 'threshold') +
-    theme_classic()
-
-threshold_output %>%
-    filter(.metric == 'j_index') %>%
-    arrange(desc(.estimate))
-
-# Distance v. threshold for not_spam
-
-threshold_output %>%
-    filter(.metric == 'distance') %>%
-    ggplot(aes(x = .threshold, y = .estimate)) +
-    geom_line() +
-    labs(y = 'Distance', x = 'threshold') +
-    theme_classic()
-
-threshold_output %>%
-    filter(.metric == 'distance') %>%
-    arrange(.estimate)
-
-log_metrics <- metric_set(accuracy,sens,yardstick::spec)
-
-final_output %>%
-    mutate(.pred_class = make_two_class_pred(.pred_not_spam, levels(spam), threshold = ___ )) %>%
-    log_metrics(truth = spam, estimate = .pred_class, event_level = 'second')
 ```
@@
   set_engine(engine = 'ranger') %>% 
-  set_args(mtry = NULL, # size of random subset of variables; default is floor(sqrt(number of total predictors))
+  set_args(mtry = 4, # size of random subset of variables; default is floor(sqrt(number of total predictors))
            trees = 1000, # Number of trees
-           min_n = 2,
+           min_n = NULL,
            probability = FALSE, # FALSE: get hard predictions (not needed for regression)
@@
 # Recipe
-data_rec <- recipe(class ~ ., data = land)
+data_rec <- recipe(flop ~ No_of_Votes, data = imdb_clean_class) %>%
+  step_naomit()
 
 # Workflows
-data_wf_mtry2 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 2)) %>%
+data_wf_mtry5 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 5)) %>%
   add_recipe(data_rec)
 
-## Create workflows for mtry = 12, 74, and 147
+## Create workflows for min_n = 10, 25, and 50
 
-data_wf_mtry12 <-
+data_wf_mtry10 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 10)) %>%
+  add_recipe(data_rec)
 
-data_wf_mtry74 <-
+data_wf_mtry25 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 25)) %>%
+  add_recipe(data_rec)
 
-data_wf_mtry147 <- 
+data_wf_mtry50 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 50)) %>%
+  add_recipe(data_rec)
 ```
@@
 set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
-data_fit_mtry2 <- fit(data_wf_mtry2, data = land)
+data_fit_mtry5 <- fit(data_wf_mtry5, data = imdb_clean_class)
 
-# Fit models for 12, 74, 147
+# Fit models for 10, 25, and 50
 set.seed(123) 
-data_fit_mtry12 <-
+data_fit_mtry10 <- fit(data_wf_mtry10, data = imdb_clean_class)
 
 set.seed(123)
-data_fit_mtry74 <-
+data_fit_mtry25 <- fit(data_wf_mtry25, data = imdb_clean_class)
 
 set.seed(123) 
-data_fit_mtry147 <- 
+data_fit_mtry50 <- fit(data_wf_mtry50, data = imdb_clean_class)
 ```
@@
 }
-
-#check out the function output
-rf_OOB_output(data_fit_mtry2,2, land %>% pull(class))
 ```
@@
 data_rf_OOB_output <- bind_rows(
-    rf_OOB_output(data_fit_mtry2,2, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry74,74, land %>% pull(class)),
-    rf_OOB_output(data_fit_mtry147,147, land %>% pull(class))
+    rf_OOB_output(data_fit_mtry5,5, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry10,10, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry25,25, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop))
 )
@@
 ```{r}
-rf_OOB_output(data_fit_mtry12,12, land %>% pull(class)) %>%
+rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop)) %>%
     conf_mat(truth = class, estimate= .pred_class)
@@
 
-model_output <-data_fit_mtry12 %>% 
+model_output <-data_fit_mtry50 %>% 
     extract_fit_engine()
@@
 model_output %>% 
-    vip(num_features = 30) + theme_classic() #based on impurity
+    vip(num_features = 10) + theme_classic() #based on impurity, 10 meaning the top 10
 
@@
 
-model_output2 <- data_wf_mtry12 %>% 
+model_output2 <- data_wf_mtry50 %>% 
   update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
-  fit(data = land) %>% 
+  fit(data = imdb_clean_class) %>% 
     extract_fit_engine()
@@
 model_output2 %>% 
-    vip(num_features = 30) + theme_classic()
+    vip(num_features = 10) + theme_classic()
 

### 2022-11-02 Final_Project_Classification_Models.Rmd
Maybe finished random forest model

@@
   mutate(success_ratio = revenue/budget) %>%
-  mutate(flop = as.factor(ifelse(success_ratio > 1, 'FALSE', 'TRUE'))) %>%
+  mutate(flop = as.factor(ifelse(success_ratio > 1.5, 'FALSE', 'TRUE'))) %>%
   filter(!is.na(flop))
@@
 # Recipe
-data_rec <- recipe(flop ~ No_of_Votes, data = imdb_clean_class) %>%
+data_rec <- recipe(flop ~ No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre, popularity, vote_average, vote_count,
+                   data = imdb_clean_class) %>%
   step_naomit()
@@
 # Workflows
-data_wf_mtry5 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 5)) %>%
+data_wf_mtry150 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 150)) %>%
   add_recipe(data_rec)
@@
 
-data_wf_mtry10 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 10)) %>%
+data_wf_mtry125 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 125)) %>%
   add_recipe(data_rec)
 
-data_wf_mtry25 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 25)) %>%
+data_wf_mtry75 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 75)) %>%
   add_recipe(data_rec)
 
-data_wf_mtry50 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 50)) %>%
+data_wf_mtry100 <- workflow() %>%
+  add_model(rf_spec %>% set_args(min_n = 100)) %>%
   add_recipe(data_rec)
@@
 set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
-data_fit_mtry5 <- fit(data_wf_mtry5, data = imdb_clean_class)
+data_fit_mtry150 <- fit(data_wf_mtry150, data = imdb_clean_class)
 
@@
 set.seed(123) 
-data_fit_mtry10 <- fit(data_wf_mtry10, data = imdb_clean_class)
+data_fit_mtry125 <- fit(data_wf_mtry125, data = imdb_clean_class)
 
 set.seed(123)
-data_fit_mtry25 <- fit(data_wf_mtry25, data = imdb_clean_class)
+data_fit_mtry75 <- fit(data_wf_mtry75, data = imdb_clean_class)
 
 set.seed(123) 
-data_fit_mtry50 <- fit(data_wf_mtry50, data = imdb_clean_class)
+data_fit_mtry100 <- fit(data_wf_mtry100, data = imdb_clean_class)
 ```
@@
 data_rf_OOB_output <- bind_rows(
-    rf_OOB_output(data_fit_mtry5,5, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry10,10, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry25,25, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop))
+    rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry75,75, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry100,100, imdb_clean_class %>% pull(flop))
 )
@@
 ```{r}
-rf_OOB_output(data_fit_mtry50,50, imdb_clean_class %>% pull(flop)) %>%
+rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)) %>%
     conf_mat(truth = class, estimate= .pred_class)
@@
 
-model_output <-data_fit_mtry50 %>% 
+model_output <-data_fit_mtry125 %>% 
     extract_fit_engine()
@@
 
-model_output2 <- data_wf_mtry50 %>% 
+model_output2 <- data_wf_mtry125 %>% 
   update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation

### 2022-11-04 Final_Project_Classification_Models.Rmd
Edits to the final classification models for HW4

@@
 ```
+
+Classification Question: Which predictor strongly influences movie revenue?
 
@@
 ```{r}
-imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000_updated.csv")
+imdb_top_1000 <- read_csv("imdb_top_1000_updated.csv")
 ```
@@
 data_wf_mtry150 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 150)) %>%
+  add_model(rf_spec %>% set_args(mtry = 150)) %>%
   add_recipe(data_rec)
@@
 data_wf_mtry125 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 125)) %>%
+  add_model(rf_spec %>% set_args(mtry = 125)) %>%
   add_recipe(data_rec)
@@
 data_wf_mtry75 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 75)) %>%
+  add_model(rf_spec %>% set_args(mtry = 75)) %>%
   add_recipe(data_rec)
@@
 data_wf_mtry100 <- workflow() %>%
-  add_model(rf_spec %>% set_args(min_n = 100)) %>%
+  add_model(rf_spec %>% set_args(mtry = 100)) %>%
   add_recipe(data_rec)
@@
           .pred_class = fit_model %>% extract_fit_engine() %>% pluck('predictions'), #OOB predictions
-          class = truth,
+          flop = truth,
           label = model_label
@@
 }
+
+rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop))
 ```
@@
     group_by(label) %>%
-    accuracy(truth = class, estimate = .pred_class)
+    accuracy(truth = flop, estimate = .pred_class)
 ```
@@
 ```
+
+# Logistic Regression
+
+```{r}
+set.seed(123)
+
+# Logistic Regression Model Spec
+logistic_spec <- logistic_reg() %>%
+    set_engine('glm') %>%
+    set_mode('classification')
+# Recipe
+logistic_rec <- recipe(flop ~ IMDB_Rating, No_of_Votes, gross,
+                   data = imdb_clean_class)
+# Workflow (Recipe + Model)
+log_wf <- workflow() %>%
+    add_recipe(logistic_rec) %>%
+    add_model(logistic_spec)
+# Fit Model
+log_fit <- fit(log_wf, data = imdb_clean_class)
+
+tidy(log_fit)
+```
+
+```{r}
+log_fit %>% tidy() %>%
+  mutate(OR = exp(estimate))
+```
+```{r}
+predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "prob"
+)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "class"
+)
+```
+
+A movie with an IMDB Rating of 5 with 500,000 votes and gross of 18 will be a flop.
+
+# Model Reflection
+
+Classification - Methods
+
+Indicate at least 2 different methods used to answer your classification research question.
+
+Random Forests and Logistic Regression
+
+Describe what you did to evaluate the models explored.
+
+?
+
+Indicate how you estimated quantitative evaluation metrics.
+
+?
+
+Describe the goals / purpose of the methods used in the overall context of your research investigations.
+
+We are attempting to determine if a movie will flop based on its difference in budget and gross.
+
+Classification - Results
+
+Summarize your final model and justify your model choice (see below for ways to justify your choice).
+
+Compare the different classification models tried in light of evaluation metrics, variable importance, and data context.
+Display evaluation metrics for different models in a clean, organized way.
+This display should include both the estimated metric as well as its standard deviation.
+(This won’t be available from OOB error estimation.
+If using OOB, don’t worry about reporting the SD.)
+Broadly summarize conclusions from looking at these evaluation metrics and their measures of uncertainty.
+
+?
+
+Classification - Conclusions - Interpret evaluation metric(s) for the final model in context.
+Does the model show an acceptable amount of error?
+- If using OOB error estimation, display the test (OOB) confusion matrix, and use it to interpret the strengths and weaknesses of the final model.
+Summarization should show evidence of acknowledging the data context in thinking about the sensibility of these results.
+
+/

### 2022-11-21 Final_Project_Classification_Models.Rmd
Updated Commits
created combined code file and updated other files (errors remain in classification model)

@@
   cSplit("Genre", sep = ",", direction = "wide") %>%
-  mutate(Gross = log(revenue))
+  mutate(Gross = log(revenue - budget))
 
@@
 # Recipe
-data_rec <- recipe(flop ~ No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre, popularity, vote_average, vote_count,
+data_rec <- recipe(flop ~ No_of_Votes + Runtime + IMDB_Rating + Meta_score + Genre_1,
                    data = imdb_clean_class) %>%
-  step_naomit()
+  step_naomit(flop, No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre_1)
 
@@
 
-?
+We underwent a random forests classification model utilizing OOB evaluation metrics. We also utilized a logistic regression model to create hard predictions.
 
@@
 
-?
+Included in the above code is OOB importance measures and logistic regression test cases.
 

### 2022-11-21 Final_Project_Code_ALL.Rmd
created combined code file and updated other files (errors remain in classification model)

--- 2022-10-17 Final_Project_Work_HW2.Rmd
@@
 ---
-title: 'STAT 253 Final Project'
-author: "Jacob, Julian, Aristo, and Emily"
-date: "October 17, 2022"
+title: "Final Project Code ALL"
+author: "Emily, Julian, Jacob, and Aristo"
+date: '2022-11-20'
 output: 
@@
 tidymodels_prefer()
+library(probably) #install.packages('probably')
+library(vip)
 ```
@@
 ```{r}
-library(readr)
-imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000.csv")
+imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000_CLEAN.csv")
 ```
@@
 imdb_clean <- imdb_top_1000 %>%
-  select(-Poster_Link, -Certificate) %>%
   cSplit("Genre", sep = ",", direction = "wide") %>%
-  mutate(Gross = log(Gross))
+  mutate(Gross = log(Revenue-Budget)) %>%
+  select(-...15)
 
@@
 imdb_clean$Runtime <- runtime_clean
+
+imdb_clean <- imdb_clean %>%
+  filter(Gross != "-Inf")
 ```
@@
 ```{r}
-full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview,
-            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
+full_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
+                   No_of_Votes + Genre_1, data = imdb_clean) %>%
     step_nzv(all_predictors()) %>% 
@@
 # Recipe with standardization (!) --> just include all these always
-data_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview,
-            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>%
+data_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
+                   No_of_Votes + Genre_1, data = imdb_clean) %>%
     step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
@@
 ```{r}
-spline_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
-    step_rm(Series_Title, Released_Year, Overview,
-            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
+spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
+                   No_of_Votes + Genre_1, data = imdb_clean) %>%
     step_nzv(all_predictors()) %>% 
@@
 
-The goal of our investigations is to accurately predict a movie's gross box office revenue based on a number of predictors.
+The goal of our investigations is to accurately predict a movie's gross box office gross revenue based on a number of predictors.
 We compared three different model types: ordinary linear regression (OLS) with all predictors, OLS using LASSO to select a subset of variables, and a GAM using splines to account for nonlinearity.
@@
 Our model can't account for that, but we are aware of it.
+
+```{r}
+imdb_clean_class <- imdb_clean %>%
+  mutate(success_ratio = Revenue/Budget) %>%
+  mutate(flop = as.factor(ifelse(success_ratio > 1.5, 'FALSE', 'TRUE'))) %>%
+  filter(!is.na(flop)) %>%
+  filter(Gross != "NaN") %>%
+  filter(success_ratio != "Inf") %>%
+  filter(Budget > 10)
+```
+
+# Bagging and Random Forests
+
+```{r}
+# Model Specification
+rf_spec <- rand_forest() %>%
+  set_engine(engine = 'ranger') %>% 
+  set_args(mtry = 4, # size of random subset of variables; default is floor(sqrt(number of total predictors))
+           trees = 1000, # Number of trees
+           min_n = NULL,
+           probability = FALSE, # FALSE: get hard predictions (not needed for regression)
+           importance = 'impurity') %>% # we'll come back to this at the end
+  set_mode('classification') # change this for regression
+
+# Recipe
+data_rec <- recipe(flop ~ No_of_Votes + Runtime + IMDB_Rating + Meta_score + Genre_1,
+                   data = imdb_clean_class) %>%
+  step_naomit(flop, No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre_1)
+
+# Workflows
+data_wf_mtry150 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 150)) %>%
+  add_recipe(data_rec)
+
+## Create workflows for min_n = 10, 25, and 50
+
+data_wf_mtry125 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 125)) %>%
+  add_recipe(data_rec)
+
+data_wf_mtry75 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 75)) %>%
+  add_recipe(data_rec)
+
+data_wf_mtry100 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 100)) %>%
+  add_recipe(data_rec)
+```
+
+```{r}
+# Fit Models
+set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
+data_fit_mtry150 <- fit(data_wf_mtry150, data = imdb_clean_class)
+
+# Fit models for 10, 25, and 50
+set.seed(123) 
+data_fit_mtry125 <- fit(data_wf_mtry125, data = imdb_clean_class)
+
+set.seed(123)
+data_fit_mtry75 <- fit(data_wf_mtry75, data = imdb_clean_class)
+
+set.seed(123) 
+data_fit_mtry100 <- fit(data_wf_mtry100, data = imdb_clean_class)
+```
+
+```{r}
+# Custom Function to get OOB predictions, true observed outcomes and add a user-provided model label
+rf_OOB_output <- function(fit_model, model_label, truth){
+    tibble(
+          .pred_class = fit_model %>% extract_fit_engine() %>% pluck('predictions'), #OOB predictions
+          flop = truth,
+          label = model_label
+      )
+}
+
+rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop))
+```
+
+```{r}
+# Evaluate OOB Metrics
+
+data_rf_OOB_output <- bind_rows(
+    rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry75,75, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry100,100, imdb_clean_class %>% pull(flop))
+)
+
+data_rf_OOB_output %>% 
+    group_by(label) %>%
+    accuracy(truth = flop, estimate = .pred_class)
+```
+
+### Evaluating the Forest
+
+```{r}
+rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)) %>%
+    conf_mat(truth = class, estimate= .pred_class)
+```
+
+### Variable Importance
+
+```{r}
+# Impurity
+
+model_output <-data_fit_mtry125 %>% 
+    extract_fit_engine()
+
+model_output %>% 
+    vip(num_features = 10) + theme_classic() #based on impurity, 10 meaning the top 10
+
+model_output %>% vip::vi() %>% head()
+model_output %>% vip::vi() %>% tail()
+```
+
+```{r}
+# Permutation
+
+model_output2 <- data_wf_mtry125 %>% 
+  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
+  fit(data = imdb_clean_class) %>% 
+    extract_fit_engine()
+
+model_output2 %>% 
+    vip(num_features = 10) + theme_classic()
+
+model_output2 %>% vip::vi() %>% head()
+model_output2 %>% vip::vi() %>% tail()
+```
+
+# Logistic Regression
+
+```{r}
+set.seed(123)
+
+# Logistic Regression Model Spec
+logistic_spec <- logistic_reg() %>%
+    set_engine('glm') %>%
+    set_mode('classification')
+# Recipe
+logistic_rec <- recipe(flop ~ IMDB_Rating, No_of_Votes, gross,
+                   data = imdb_clean_class)
+# Workflow (Recipe + Model)
+log_wf <- workflow() %>%
+    add_recipe(logistic_rec) %>%
+    add_model(logistic_spec)
+# Fit Model
+log_fit <- fit(log_wf, data = imdb_clean_class)
+
+tidy(log_fit)
+```
+
+```{r}
+log_fit %>% tidy() %>%
+  mutate(OR = exp(estimate))
+```
+```{r}
+predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "prob"
+)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "class"
+)
+```

### 2022-11-28 ClusteringModel.Rmd
Started Clustering (K-Means)

---
title: "Clustering Model"
author: "Emily Bergin"
date: '2022-11-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

# Library Statements

```{r}
library(dplyr)
library(purrr)
library(ggplot2)
library(ISLR)
library(readr)
library(tidymodels)
library(stringr)
library(lubridate)
```

# Read in Data

```{r}
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000_CLEAN.csv")
```

# Data Cleaning

```{r}
imdb_clean <- imdb_top_1000 %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = log(Revenue-Budget)) %>%
  select(-...15)

runtime_clean <- imdb_top_1000$Runtime %>%
  str_replace(" min", "") %>%
  as.numeric()

imdb_clean$Runtime <- runtime_clean

imdb_clean <- imdb_clean %>%
  filter(Gross != "-Inf") %>%
  filter(!is.na(Gross)) %>%
  filter(!is.na(Budget))
```

### K-Means Clustering

```{r}
# Select just the bill length and depth variables
imdb_sub <- imdb_clean %>%
    select(Budget, Gross)

# Run k-means for k = centers = 3
set.seed(253)
kclust_k10 <- kmeans(scale(imdb_sub), centers = 10)

# Display the cluter assignments
kclust_k10$cluster

# Add a variable (kclust_3) to the original dataset 
# containing the cluster assignments
imdb_clean <- imdb_clean %>%
    mutate(kclust_10 = factor(kclust_k10$cluster))
```

```{r}
# Visualize the cluster assignments on the original scatterplot
imdb_clean %>%
  ggplot(aes(x = Budget, y = Gross, color = kclust_10)) +
    geom_point() + theme_classic()
```

## Interpreting the Clusters

```{r}
imdb_clean %>%
    group_by(kclust_10) %>%
    summarize(across(c(Gross, Budget), mean))
```

### 2022-11-28 Final_Project_Code_ALL.Rmd
Started Clustering (K-Means)

@@
 library(splitstackshape)
-library(tidymodels)
 library(lubridate)

### 2022-11-29 ClusteringModel.Rmd
Worked on K-Means and started Hierarchial Clustering

@@
 library(lubridate)
+library(splitstackshape)
 ```
@@
 
+```{r}
+# Data-specific function to cluster and calculate total within-cluster SS
+imdb_cluster_ss <- function(k){
+    # Perform clustering
+    kclust <- kmeans(scale(imdb_sub), centers = k)
+
+    # Return the total within-cluster sum of squares
+    return(kclust$tot.withinss)
+}
+
+tibble(
+    k = 1:15,
+    tot_wc_ss = purrr::map_dbl(1:15, imdb_cluster_ss)
+) %>% 
+    ggplot(aes(x = k, y = tot_wc_ss)) +
+    geom_point() + 
+    labs(x = "Number of clusters",y = 'Total within-cluster sum of squares') + 
+    theme_classic()
+```
+
+```{r}
+kclust_k8 <- kmeans(scale(imdb_sub), centers = 8)
+
+# Display the cluter assignments
+kclust_k8$cluster
+
+# Add a variable (kclust_3) to the original dataset 
+# containing the cluster assignments
+imdb_clean <- imdb_clean %>%
+    mutate(kclust_8 = factor(kclust_k8$cluster))
+```
+
+```{r}
+# Visualize the cluster assignments on the original scatterplot
+imdb_clean %>%
+  ggplot(aes(x = Budget, y = Gross, color = kclust_8)) +
+    geom_point() + theme_classic()
+```
+
+*Pick either k = 8 or k = 10 --> there are 7 genres with larger n and 13 total genres.
+Film noir is fancy way of saying crime drama (ex.
+Knives Out).
+One thing to note is a significant number of movies have Genre_2 listed as Family Mystery and Horror (and many have one of the main genres listed as genre 2 as well).
+What is a good way to summarize both Genre 1 and 2?*
+
+```{r}
+imdb_clean %>%
+  count(Genre_1)
+
+imdb_clean %>%
+  count(Genre_2)
+```
+
 ## Interpreting the Clusters
@@
   summarize(across(c(Gross, Budget), mean))
+
+imdb_clean %>%
+  group_by(kclust_8) %>%
+  count(Genre_1)
+
+imdb_clean %>%
+  group_by(kclust_8) %>%
+  count(Genre_2)
+
+imdb_clean%>%
+  count(kclust_8)
 ```
+
+### Hierarchial Clustering
+
+```{r}
+# Random subsample of 50 penguins
+set.seed(253)
+imdb_hc <- imdb_clean %>%
+    slice_sample(n = 25)
+
+# Select the variables to be used in clustering
+imdb_hc_sub <- imdb_hc %>%
+    select(Gross, Budget)
+
+# Summary statistics for the variables
+summary(imdb_hc_sub)
+
+# Compute a distance matrix on the scaled data
+dist_mat_scaled <- dist(scale(imdb_hc_sub))
+```
+
+```{r}
+imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")
+
+# Plot dendrogram
+plot(imdb_hc_avg)
+```
+
+```{r}
+
+plot(imdb_hc_avg, labels = imdb_hc$Genre_1)
+
+plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2))
+```

### 2022-11-29 Final_Project_Code_ALL.Rmd
Worked on classification models

@@
 imdb_clean <- imdb_clean %>%
-  filter(Gross != "-Inf")
+  filter(Gross != "-Inf") %>%
+  drop_na(Gross, Budget)
 ```
@@
   mutate(success_ratio = Revenue/Budget) %>%
-  mutate(flop = as.factor(ifelse(success_ratio > 1.5, 'FALSE', 'TRUE'))) %>%
-  filter(!is.na(flop)) %>%
-  filter(Gross != "NaN") %>%
-  filter(success_ratio != "Inf") %>%
-  filter(Budget > 10)
+  mutate(flop = as.factor(ifelse(success_ratio > 2, 'FALSE', 'TRUE'))) %>%
+  drop_na(flop, No_of_Votes,Runtime, IMDB_Rating,Meta_score,Genre_1)
+  # filter(!is.na(flop)) %>%
+  # filter(Gross != "NaN") %>%
+  # filter(success_ratio != "Inf") %>%
+  # filter(Budget > 10)
 ```
@@
   set_engine(engine = 'ranger') %>% 
-  set_args(mtry = 4, # size of random subset of variables; default is floor(sqrt(number of total predictors))
-           trees = 1000, # Number of trees
+  set_args(trees = 1000, # Number of trees
            min_n = NULL,
@@
 # Workflows
-data_wf_mtry150 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 150)) %>%
+data_wf_mtry3 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 3)) %>%
+  add_recipe(data_rec)
+
+data_wf_mtry4 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 4)) %>%
   add_recipe(data_rec)
@@
 
-data_wf_mtry125 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 125)) %>%
-  add_recipe(data_rec)
-
-data_wf_mtry75 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 75)) %>%
-  add_recipe(data_rec)
-
-data_wf_mtry100 <- workflow() %>%
-  add_model(rf_spec %>% set_args(mtry = 100)) %>%
+data_wf_mtry5 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 5)) %>%
   add_recipe(data_rec)
@@
 set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
-data_fit_mtry150 <- fit(data_wf_mtry150, data = imdb_clean_class)
-
-# Fit models for 10, 25, and 50
-set.seed(123) 
-data_fit_mtry125 <- fit(data_wf_mtry125, data = imdb_clean_class)
+data_fit_mtry3 <- fit(data_wf_mtry3, data = imdb_clean_class)
 
 set.seed(123) 
-data_fit_mtry75 <- fit(data_wf_mtry75, data = imdb_clean_class)
+data_fit_mtry4 <- fit(data_wf_mtry4, data = imdb_clean_class)
 
 set.seed(123)
-data_fit_mtry100 <- fit(data_wf_mtry100, data = imdb_clean_class)
+data_fit_mtry5 <- fit(data_wf_mtry5, data = imdb_clean_class)
 ```
@@
 }
-
-rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop))
 ```
@@
 data_rf_OOB_output <- bind_rows(
-    rf_OOB_output(data_fit_mtry150,150, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry75,75, imdb_clean_class %>% pull(flop)),
-    rf_OOB_output(data_fit_mtry100,100, imdb_clean_class %>% pull(flop))
+    rf_OOB_output(data_fit_mtry3,3, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry5,5, imdb_clean_class %>% pull(flop))
 )
@@
 ```{r}
-rf_OOB_output(data_fit_mtry125,125, imdb_clean_class %>% pull(flop)) %>%
-    conf_mat(truth = class, estimate= .pred_class)
+rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
+    conf_mat(truth = flop, estimate= .pred_class)
 ```
@@
 
-model_output <-data_fit_mtry125 %>% 
+model_output <-data_fit_mtry4 %>% 
     extract_fit_engine()
@@
 
-model_output2 <- data_wf_mtry125 %>% 
+model_output2 <- data_wf_mtry4 %>% 
   update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
@@
     set_mode('classification')
+
 # Recipe
-logistic_rec <- recipe(flop ~ IMDB_Rating, No_of_Votes, gross,
+logistic_rec <- recipe(flop ~ No_of_Votes + Runtime + IMDB_Rating + Genre_1,
                    data = imdb_clean_class)
+
 # Workflow (Recipe + Model)
@@
     add_model(logistic_spec)
+
 # Fit Model
@@
 ```
+
 ```{r}
-predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "prob"
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "prob"
 )
@@
 ```{r}
-predict(log_fit, new_data = data.frame(IMDB_Rating = 5, No_of_Votes = 500000, gross = 18), type = "class"
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "class"
 )

### 2022-11-30 Final_Project_Code_ALL.Rmd
Worked on evaluation metrics and choosing threshold for log model

@@
 ```
+
+```{r}
+# Creation of CV Folds
+data_cv10_class <- vfold_cv(imdb_clean_class, v = 10)
+```
+
+# Recipes and Workflows
+
+```{r}
+full_log_wf <- workflow() %>%
+    add_recipe(logistic_rec) %>%
+    add_model(logistic_spec)
+
+log_model <- fit(full_log_wf, data = imdb_clean_class)
+
+log_modelcv <- fit_resamples(full_log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))
+
+log_modelcv %>%
+  collect_metrics()
+```
+
+```{r}
+# Soft Predictions on Training Data
+final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)
+
+final_output %>%
+  ggplot(aes(x = flop, y = .pred_TRUE)) +
+  geom_boxplot()
+```
+
+```{r}
+# Use soft predictions
+final_output %>%
+    roc_curve(flop,.pred_TRUE,event_level = 'second') %>%
+    autoplot()
+```
+
+```{r}
+# thresholds in terms of reference level
+threshold_output <- final_output %>%
+    threshold_perf(truth = flop, estimate = .pred_FALSE, thresholds = seq(0,1,by=.01))
+
+# J-index v. threshold for no flop
+threshold_output %>%
+    filter(.metric == 'j_index') %>%
+    ggplot(aes(x = .threshold, y = .estimate)) +
+    geom_line() +
+    labs(y = 'J-index', x = 'threshold') +
+    theme_classic()
+```
+
+```{r}
+threshold_output %>%
+    filter(.metric == 'j_index') %>%
+    arrange(desc(.estimate))
+```
+
+```{r}
+# Distance v. threshold for not_spam
+
+threshold_output %>%
+    filter(.metric == 'distance') %>%
+    ggplot(aes(x = .threshold, y = .estimate)) +
+    geom_line() +
+    labs(y = 'Distance', x = 'threshold') +
+    theme_classic()
+```
+
+```{r}
+threshold_output %>%
+    filter(.metric == 'distance') %>%
+    arrange(.estimate)
+```
+
+```{r}
+log_metrics <- metric_set(accuracy,sens,yardstick::spec)
+
+final_output %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
+    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
+
+final_output %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
+  conf_mat(truth = flop, estimate = .pred_class)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "prob"
+)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "class"
+)
+```
+
+*How to add threshold here?*

### 2022-11-30 Final_Project_Code_ALL.Rmd
office hours

@@
 final_output %>%
-    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
     log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
@@
 final_output %>%
-  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
   conf_mat(truth = flop, estimate = .pred_class)
@@
 predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
-                                        Genre_1 = "Drama"), type = "class"
+                                        Genre_1 = "Drama"), type = "class", threshold = .12
 )

### 2022-12-02 Draft_Final_Code.Rmd
Started organizing final code appendix

---
title: "Final Project Code ALL"
author: "Emily, Julian, Jacob, and Aristo"
date: '2022-11-20'
output: 
  html_document:
    df_print: paged
    toc: true
    code_download: true
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

# Library Statements

```{r}
library(ISLR)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
library(stringr)
library(splitstackshape)
library(lubridate)
library(rpart.plot)
library(cluster)
library(forcats)
tidymodels_prefer()
library(probably) #install.packages('probably')
library(vip)
```

# Dataset

```{r}
imdb_top_1000 <- read_csv("~/Desktop/Statistical Machine Learning/R Files/Final Project/imdb_top_1000_CLEAN.csv")
```

## Data Cleaning

```{r}
imdb_clean <- imdb_top_1000 %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = log(Revenue-Budget)) %>%
  select(-...15)

runtime_clean <- imdb_top_1000$Runtime %>%
  str_replace(" min", "") %>%
  as.numeric()

imdb_clean$Runtime <- runtime_clean

imdb_clean <- imdb_clean %>%
  filter(Gross != "-Inf") %>%
  drop_na(Gross, Budget)
```

## Data

```{r}
head(imdb_clean)
```

# Regression Models

## Linear Regression Model

### Creation of CV Folds

```{r}
data_cv10 <- vfold_cv(imdb_clean, v = 10)
```

### Model Spec, Recipes, and Workflows for Linear Regression Model

```{r}
# Model Spec

lm_spec <-
    linear_reg() %>% 
    set_engine(engine = 'lm') %>% 
    set_mode('regression')

# Recipe

full_lm_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross, Runtime, IMDB_Rating, Meta_score, No_of_Votes)

# Workflow

full_lm_wf <- workflow() %>%
    add_recipe(full_lm_rec) %>%
    add_model(lm_spec)
```

### Fit Preliminary Model

```{r}
full_lm_model <- fit(full_lm_wf, data = imdb_clean)

full_lm_model %>% tidy()
```

### Obtain Evaluation Metrics for Preliminary Model

```{r}
full_lm_modelcv <- fit_resamples(full_lm_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))

full_lm_modelcv %>%
  collect_metrics()
```

### Perform LASSO for Subset Selection

```{r}
# Lasso Model Spec with tune

lm_lasso_spec_tune <- 
  linear_reg() %>%
  set_args(mixture = 1, penalty = tune()) %>%   # mixture = 1 indicates Lasso
  set_engine(engine = 'glmnet') %>%             
  set_mode('regression')

# Recipe

data_rec_lasso <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>%                # removes variables with the same value (don't want duplicates)
    step_novel(all_nominal_predictors()) %>%      # important if you have rare categorical variables 
    step_normalize(all_numeric_predictors()) %>%  # standardization important step for LASSO
    step_dummy(all_nominal_predictors()) %>%      # creates indicator variables for categorical variables
    step_naomit(Gross, Runtime, IMDB_Rating,      # omit any NA values
                Meta_score, No_of_Votes)

# Workflow

lasso_wf_tune <- workflow() %>% 
  add_recipe(data_rec_lasso) %>%
  add_model(lm_lasso_spec_tune)

# Tune Model (trying a variety of values of Lambda penalty)

penalty_grid <- grid_regular(
  penalty(range = c(-3, 1)),
  levels = 30)

tune_res <- tune_grid(
  lasso_wf_tune, 
  resamples = data_cv10, 
  metrics = metric_set(rmse, mae),
  grid = penalty_grid 
)

# Visualize Model Evaluation Metrics from Tuning

autoplot(tune_res) + theme_classic()
```

### 2022-12-02 Draft_Final_Code.Rmd
worked on linear regression more

@@
 autoplot(tune_res) + theme_classic()
+
+# Collect CV Metrics and Select Best Model
+
+# Summarize Model Evaluation Metrics (CV)
+lasso_mod <- collect_metrics(tune_res) %>%
+  filter(.metric == 'rmse') %>%
+  select(penalty, rmse = mean)
+
+best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value
+
+lasso_mod
 ```
+
+### Fit Final Model
+
+```{r}
+# Fit Final Model
+
+final_wf <- finalize_workflow(lasso_wf_tune, best_penalty) # incorporates penalty value to workflow
+
+final_fit <- fit(final_wf, data = imdb_clean)
+
+lasso_fit <- fit_resamples(final_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))
+
+tidy(final_fit)
+
+# Final ("best") model predictors and coefficients
+
+final_fit %>% tidy() %>% filter(estimate != 0)
+```
+
+### Visualize Residuals
+
+```{r}
+lasso_mod_out <- final_fit %>%
+    predict(new_data = imdb_clean) %>%
+    bind_cols(imdb_clean) %>%
+    mutate(resid = Gross - .pred)
+
+ggplot(lasso_mod_out, aes(x = .pred, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = Runtime, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = IMDB_Rating, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out, aes(x = No_of_Votes, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+```
+
+## GAM Using Splines
+
+```{r}
+# Build the GAM
+
+gam_spec <- 
+  gen_additive_mod() %>%
+  set_engine(engine = 'mgcv') %>%
+  set_mode('regression')
+
+gam_mod <- fit(gam_spec,
+    Gross ~ s(Runtime) + IMDB_Rating + s(Meta_score) + s(No_of_Votes) + Genre_1,
+    data = imdb_clean 
+)
+
+```
+
+````{r}
+# Diagnostics: Check to see if the number of knots is large enough (if p-value is low, increase number of knots)
+
+gam_mod %>% pluck('fit') %>% mgcv::gam.check()
+
+gam_mod %>% pluck('fit') %>% summary() 
+```
+
+```{r}
+# Visualize: Look at the estimated non-linear functions
+
+gam_mod %>% pluck('fit') %>% plot()
+```

### 2022-12-06 Draft_Final_Code.Rmd
rough draft for final code

@@
 ```
+
+```{r}
+spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
+                   No_of_Votes + Genre_1, data = imdb_clean) %>%
+    step_nzv(all_predictors()) %>% 
+    step_normalize(all_numeric_predictors()) %>% 
+    step_dummy(all_nominal_predictors()) %>%
+    step_naomit(Gross) %>%
+    step_ns(Runtime, deg_free = 2) %>%
+    step_ns(No_of_Votes, deg_free = 6)
+
+spline_rec %>% prep(imdb_clean) %>% juice()
+```
+
+```{r}
+# Use the edf (round to integer) from above to create a recipe by adding step_ns() for the variables you want model with a non-linear relationship and do CV.
+Compare this model to one without any splines.
+
+lm_spec_gam <-
+  linear_reg() %>%
+  set_engine(engine = 'lm') %>%
+  set_mode('regression')
+
+spline_wf <- workflow() %>%
+    add_model(lm_spec) %>%
+    add_recipe(spline_rec)
+
+cv_output <- fit_resamples( 
+  spline_wf, # workflow
+  resamples = data_cv10, # cv folds
+  metrics = metric_set(mae,rmse,rsq)
+)
+
+cv_output %>% collect_metrics()
+
+```
+
+```{r}
+new_mod <- spline_wf %>%
+  fit(data = imdb_clean)
+
+new_mod %>%
+  tidy()
+
+new_mod %>% 
+  tidy() %>% 
+  arrange(desc(abs(statistic)))
+
+new_modcv <- fit_resamples(spline_wf, resamples = data_cv10, metrics = metric_set(mae, rmse, rsq))
+```
+
+# Variable Importance for GAM
+
+```{r}
+# Lasso Model Spec with tune
+gam_lasso_spec_tune <- 
+  linear_reg() %>%
+  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
+  set_engine(engine = 'glmnet') %>% #note we are using a different engine
+  set_mode('regression')
+
+# Recipe with standardization (!) --> just include all these always
+data_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
+                   No_of_Votes + Genre_1, data = imdb_clean) %>%
+    step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
+    step_novel(all_nominal_predictors()) %>% # important if you have rare categorical variables 
+    step_normalize(all_numeric_predictors()) %>%  # super important standardization step for LASSO
+    step_dummy(all_nominal_predictors()) %>%  # creates indicator variables for categorical variables
+    step_naomit(Gross)
+
+# Workflow (Recipe + Model)
+lasso_wf_tune1 <- workflow() %>% 
+  add_recipe(data_rec) %>%
+  add_model(gam_lasso_spec_tune)
+
+# Tune Model (trying a variety of values of Lambda penalty)
+penalty_grid <- grid_regular(
+  penalty(range = c(-3, 1)),
+  levels = 30)
+
+tune_res1 <- tune_grid( # new function for tuning parameters
+  lasso_wf_tune1, # workflow
+  resamples = data_cv10, # cv folds
+  metrics = metric_set(rmse, mae),
+  grid = penalty_grid # penalty grid defined above
+)
+
+# Visualize Model Evaluation Metrics from Tuning
+autoplot(tune_res1) + theme_classic()
+```
+
+# Collect CV Metrics and Select Best Model
+
+```{r}
+
+# Summarize Model Evaluation Metrics (CV)
+collect_metrics(tune_res) %>%
+  filter(.metric == 'rmse') %>% # or choose mae
+  select(penalty, rmse = mean)
+
+best_penalty1 <- select_best(tune_res1, metric = 'rmse') # choose penalty value based on lowest mae or rmse
+```
+
+# Fit Final Model
+
+```{r}
+
+# Fit Final Model
+final_wf1 <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow
+
+final_fit1 <- fit(final_wf1, data = imdb_clean)
+
+tidy(final_fit1)
+```
+
+```{r}
+# Final ("best") model predictors and coefficients
+
+final_fit1 %>% tidy() %>% filter(estimate != 0)
+```
+
+# Visualize Residuals
+
+```{r}
+
+# Visualize Residuals
+lasso_mod_out1 <- new_mod %>%
+    predict(new_data = imdb_clean) %>%
+    bind_cols(imdb_clean) %>%
+    mutate(resid = Gross - .pred)
+
+ggplot(lasso_mod_out1, aes(x = .pred, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out1, aes(x = Runtime, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out1, aes(x = IMDB_Rating, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+
+ggplot(lasso_mod_out1, aes(x = No_of_Votes, y = resid)) +
+    geom_point() +
+    geom_smooth() +
+    geom_hline(yintercept = 0, color = "red") + 
+    theme_classic()
+```
+
+# Comparing Model Performance
+
+```{r}
+full_lm_modelcv %>% collect_metrics() #OLS
+```
+
+```{r}
+lasso_fit %>% collect_metrics() #LASSO
+```
+
+```{r}
+new_modcv %>% collect_metrics() #GAM
+```
+
+# Bagging and Random Forests
+
+```{r}
+imdb_clean_class <- imdb_clean %>%
+  mutate(success_ratio = Revenue/Budget) %>%
+  mutate(flop = as.factor(ifelse(success_ratio > 2, 'FALSE', 'TRUE'))) %>%
+  drop_na(flop, No_of_Votes,Runtime, IMDB_Rating,Meta_score,Genre_1)
+```
+
+```{r}
+# Model Specification
+rf_spec <- rand_forest() %>%
+  set_engine(engine = 'ranger') %>% 
+  set_args(trees = 1000, # Number of trees
+           min_n = NULL,
+           probability = FALSE,
+           importance = 'impurity') %>%
+  set_mode('classification')
+
+# Recipe
+data_rec <- recipe(flop ~ No_of_Votes + Runtime + IMDB_Rating + Meta_score + Genre_1,
+                   data = imdb_clean_class) %>%
+  step_naomit(flop, No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre_1)
+
+# Create Workflows
+data_wf_mtry3 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 3)) %>%
+  add_recipe(data_rec)
+
+data_wf_mtry4 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 4)) %>%
+  add_recipe(data_rec)
+
+data_wf_mtry5 <- workflow() %>%
+  add_model(rf_spec %>% set_args(mtry = 5)) %>%
+  add_recipe(data_rec)
+```
+
+```{r}
+# Fit Models
+set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
+data_fit_mtry3 <- fit(data_wf_mtry3, data = imdb_clean_class)
+
+set.seed(123) 
+data_fit_mtry4 <- fit(data_wf_mtry4, data = imdb_clean_class)
+
+set.seed(123)
+data_fit_mtry5 <- fit(data_wf_mtry5, data = imdb_clean_class)
+```
+
+```{r}
+# Custom Function to get OOB predictions, true observed outcomes and add a user-provided model label
+rf_OOB_output <- function(fit_model, model_label, truth){
+    tibble(
+          .pred_class = fit_model %>% extract_fit_engine() %>% pluck('predictions'), #OOB predictions
+          flop = truth,
+          model = model_label
+      )
+}
+```
+
+```{r}
+# Evaluate OOB Metrics
+
+data_rf_OOB_output <- bind_rows(
+    rf_OOB_output(data_fit_mtry3,3, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)),
+    rf_OOB_output(data_fit_mtry5,5, imdb_clean_class %>% pull(flop))
+)
+
+data_rf_OOB_output %>% 
+    group_by(model) %>%
+    accuracy(truth = flop, estimate = .pred_class)
+
+data_rf_OOB_output %>% 
+  group_by(model) %>%
+  accuracy(truth = flop, estimate = .pred_class) %>%
+  mutate(mtry = as.numeric(stringr::str_replace(model,'mtry',''))) %>%
+  ggplot(aes(x = mtry, y = .estimate )) + 
+  geom_point() +
+  geom_line() +
+  theme_classic()
+```
+
+### Evaluating the Forest
+
+```{r}
+rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
+    conf_mat(truth = flop, estimate= .pred_class)
+```
+
+### Variable Importance
+
+```{r}
+# Impurity
+
+model_output <-data_fit_mtry4 %>% 
+    extract_fit_engine()
+
+model_output %>% 
+    vip(num_features = 10) + theme_classic() #based on impurity, 10 meaning the top 10
+
+model_output %>% vip::vi() %>% head()
+model_output %>% vip::vi() %>% tail()
+```
+
+```{r}
+# Permutation
+
+model_output2 <- data_wf_mtry4 %>% 
+  update_model(rf_spec %>% set_args(importance = "permutation")) %>% #based on permutation
+  fit(data = imdb_clean_class) %>% 
+    extract_fit_engine()
+
+model_output2 %>% 
+    vip(num_features = 10) + theme_classic()
+
+model_output2 %>% vip::vi() %>% head()
+model_output2 %>% vip::vi() %>% tail()
+```
+```{r}
+ggplot(imdb_clean_class, aes(x = flop, y = No_of_Votes)) +
+    geom_violin() + theme_classic()
+
+ggplot(imdb_clean_class, aes(x = flop, y = Runtime)) +
+    geom_violin() + theme_classic()
+
+ggplot(imdb_clean_class, aes(x = flop, y = IMDB_Rating)) +
+    geom_violin() + theme_classic()
+
+ggplot(imdb_clean_class, aes(x = flop, y = Meta_score)) +
+    geom_violin() + theme_classic()
+```
+
+# Logistic Regression
+
+```{r}
+set.seed(123)
+
+# Logistic Regression Model Spec
+logistic_spec <- logistic_reg() %>%
+    set_engine('glm') %>%
+    set_mode('classification')
+
+# Recipe
+logistic_rec <- recipe(flop ~ No_of_Votes + Runtime + IMDB_Rating + Genre_1,
+                   data = imdb_clean_class)
+
+# Workflow (Recipe + Model) for Full Log Model
+log_wf <- workflow() %>%
+    add_recipe(logistic_rec) %>%
+    add_model(logistic_spec)
+
+# Fit Model
+log_fit <- fit(log_wf, data = imdb_clean_class)
+
+tidy(log_fit)
+```
+
+```{r}
+log_fit %>% tidy() %>%
+  mutate(OR = exp(estimate))
+```
+
+*Ask Bryan about relevel factor... do we need it?*
+
+```{r}
+# Creation of CV Folds
+data_cv10_class <- vfold_cv(imdb_clean_class, v = 10)
+```
+
+# Recipes and Workflows
+
+```{r}
+full_log_wf <- workflow() %>%
+  add_recipe(logistic_rec) %>%
+  add_model(logistic_spec)
+
+log_model <- fit(full_log_wf, data = imdb_clean_class)
+
+log_modelcv <- fit_resamples(full_log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))
+
+log_modelcv %>%
+  collect_metrics()
+```
+
+```{r}
+# Soft Predictions on Training Data
+final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)
+
+final_output %>%
+  ggplot(aes(x = flop, y = .pred_TRUE)) +
+  geom_boxplot()
+```
+
+```{r}
+# Use soft predictions
+final_output %>%
+    roc_curve(flop,.pred_TRUE,event_level = 'second') %>%
+    autoplot()
+```
+
+```{r}
+# thresholds in terms of reference level
+threshold_output <- final_output %>%
+    threshold_perf(truth = flop, estimate = .pred_FALSE, thresholds = seq(0,1,by=.01))
+
+# J-index v. threshold for no flop
+threshold_output %>%
+    filter(.metric == 'j_index') %>%
+    ggplot(aes(x = .threshold, y = .estimate)) +
+    geom_line() +
+    labs(y = 'J-index', x = 'threshold') +
+    theme_classic()
+```
+
+```{r}
+threshold_output %>%
+    filter(.metric == 'j_index') %>%
+    arrange(desc(.estimate))
+```
+
+```{r}
+# Distance v. threshold for not_spam
+
+threshold_output %>%
+    filter(.metric == 'distance') %>%
+    ggplot(aes(x = .threshold, y = .estimate)) +
+    geom_line() +
+    labs(y = 'Distance', x = 'threshold') +
+    theme_classic()
+```
+
+```{r}
+threshold_output %>%
+    filter(.metric == 'distance') %>%
+    arrange(.estimate)
+```
+
+```{r}
+log_metrics <- metric_set(accuracy,sens,yardstick::spec)
+
+final_output %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
+    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
+
+final_output %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
+  conf_mat(truth = flop, estimate = .pred_class)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "prob"
+)
+```
+
+```{r}
+predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
+                                        Genre_1 = "Drama"), type = "class"
+)
+```
+
+*Must manually calculate hard prediction*
+
+### K-Means Clustering
+
+```{r}
+ggplot(imdb_clean, aes(x = Budget, y = Runtime)) + 
+  geom_point() + theme_classic()
+
+ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
+  geom_point() + theme_classic()
+
+ggplot(imdb_clean, aes(x = No_of_Votes, y = Runtime)) + 
+  geom_point() + theme_classic()
+
+ggplot(imdb_clean, aes(x = Gross, y = No_of_Votes)) + 
+  geom_point() + theme_classic()
+```
+
+```{r}
+# Select just the bill length and depth variables
+imdb_sub <- imdb_clean %>%
+    select(Budget, Runtime)
+
+# Run k-means for k = centers = 3
+set.seed(253)
+kclust_k10 <- kmeans(scale(imdb_sub), centers = 10)
+
+# Display the cluter assignments
+kclust_k10$cluster
+
+# Add a variable (kclust_3) to the original dataset 
+# containing the cluster assignments
+imdb_clean <- imdb_clean %>%
+    mutate(kclust_10 = factor(kclust_k10$cluster))
+```
+
+```{r}
+# Visualize the cluster assignments on the original scatterplot
+imdb_clean %>%
+  ggplot(aes(x = Budget, y = Runtime, color = kclust_10)) +
+    geom_point() + theme_classic()
+```
+
+```{r}
+# Data-specific function to cluster and calculate total within-cluster SS
+imdb_cluster_ss <- function(k){
+    # Perform clustering
+    kclust <- kmeans(scale(imdb_sub), centers = k)
+
+    # Return the total within-cluster sum of squares
+    return(kclust$tot.withinss)
+}
+
+tibble(
+    k = 1:15,
+    tot_wc_ss = purrr::map_dbl(1:15, imdb_cluster_ss)
+) %>% 
+    ggplot(aes(x = k, y = tot_wc_ss)) +
+    geom_point() + 
+    labs(x = "Number of clusters",y = 'Total within-cluster sum of squares') + 
+    theme_classic()
+```
+
+```{r}
+kclust_k8 <- kmeans(scale(imdb_sub), centers = 8)
+
+# Display the cluter assignments
+kclust_k8$cluster
+
+# Add a variable (kclust_3) to the original dataset 
+# containing the cluster assignments
+imdb_clean <- imdb_clean %>%
+    mutate(kclust_8 = factor(kclust_k8$cluster))
+```
+
+```{r}
+# Visualize the cluster assignments on the original scatterplot
+imdb_clean %>%
+  ggplot(aes(x = Budget, y = Runtime, color = kclust_8)) +
+    geom_point() + theme_classic()
+```
+
+*Pick either k = 8 or k = 10 --> there are 7 genres with larger n and 13 total genres.
+Film noir is fancy way of saying crime drama (ex.
+Knives Out).
+One thing to note is a significant number of movies have Genre_2 listed as Family Mystery and Horror (and many have one of the main genres listed as genre 2 as well).
+What is a good way to summarize both Genre 1 and 2?*
+
+```{r}
+imdb_clean %>%
+  count(Genre_1)
+
+imdb_clean %>%
+  count(Genre_2)
+```
+
+## Interpreting the Clusters
+
+```{r}
+imdb_clean %>%
+  group_by(kclust_10) %>%
+  summarize(across(c(Gross, Budget), mean))
+
+imdb_clean %>%
+  group_by(kclust_8) %>%
+  count(Genre_1)
+
+imdb_clean %>%
+  group_by(kclust_8) %>%
+  count(Genre_2)
+
+imdb_clean%>%
+  count(kclust_8)
+```
+
+### Hierarchial Clustering
+
+```{r}
+# Random subsample of 50 penguins
+set.seed(253)
+imdb_hc <- imdb_clean %>%
+    slice_sample(n = 25)
+
+# Select the variables to be used in clustering
+imdb_hc_sub <- imdb_hc %>%
+    select(Gross, Budget)
+
+# Summary statistics for the variables
+summary(imdb_hc_sub)
+
+# Compute a distance matrix on the scaled data
+dist_mat_scaled <- dist(scale(imdb_hc_sub))
+```
+
+```{r}
+imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")
+
+# Plot dendrogram
+plot(imdb_hc_avg)
+```
+
+```{r}
+
+plot(imdb_hc_avg, labels = imdb_hc$Genre_1)
+
+plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2))
+```
+
+```{r}
+imdb_clean <- imdb_clean %>%
+    mutate(
+        hclust_height = factor(cutree(imdb_hc_avg, h = 1.25)), # Cut at height (h) 3
+        hclust_num = factor(cutree(imdb_hc_avg, k = 5)) # Cut into 6 clusters (k)
+    )
+
+plot(imdb_hc_avg, labels = imdb_clean$hclust_height)
+```

### 2022-12-08 Draft_Final_Code.Rmd
Almost finalized linear regression code

@@
 
-## Linear Regression Model
+## Ordinary Linear Regression Model
 
@@
 
-### Fit Preliminary Model
+### Fit Full Model
 
@@
 
-### Obtain Evaluation Metrics for Preliminary Model
+### Obtain Evaluation Metrics for Full Model
 
@@
 
-### Perform LASSO for Subset Selection
+## Perform LASSO for Subset Selection
 
@@
 
-best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value
+# Choose penalty value
+best_penalty <- select_best(tune_res, metric = 'rmse')
 
@@
 
-### Fit Final Model
+### Fit Final LASSO Model
 
@@
 
-### Visualize Residuals
+### Obtain Evaluation Metrics for Full Model
+
+```{r}
+lasso_fit %>%
+  collect_metrics()
+```
+
+### Visualize Residuals for LASSO Model
 
@@
 
-## GAM Using Splines
+## GAM with Splines (TidyModels)
+
+### Build the GAM
 
@@
 
-gam_mod <- fit(gam_spec,
-    Gross ~ s(Runtime) + IMDB_Rating + s(Meta_score) + s(No_of_Votes) + Genre_1,
+gam_mod1 <- fit(gam_spec,
+    Gross ~ s(Runtime) + s(IMDB_Rating) + Meta_score + s(No_of_Votes) + Genre_1,
     data = imdb_clean 
@@
 
+### Run Diagnostics
+
 ````{r}
@@
 
-gam_mod %>% pluck('fit') %>% mgcv::gam.check()
+gam_mod1 %>% pluck('fit') %>% mgcv::gam.check()
+```
 
-gam_mod %>% pluck('fit') %>% summary() 
+```{r}
+# Diagnostics: Check to see if the number of knots is large enough
+
+gam_mod1 %>% pluck('fit') %>% summary() 
 ```
+
+### Visualization for Non-Linear Functions
 
@@
 
-gam_mod %>% pluck('fit') %>% plot()
+gam_mod1 %>% pluck('fit') %>% plot()
 ```
+
+### Evaluation Metrics
+
+```{r}
+gam1_output <- gam_mod1%>% 
+    predict(new_data = imdb_clean) %>%
+    bind_cols(imdb_clean) %>%
+    mutate(resid = Gross - .pred)
+
+gam1_output %>%
+    rmse(truth = Gross, estimate = .pred)
+
+gam1_output %>%
+    rsq(truth = Gross, estimate = .pred)
+```
+
+## GAM with Splines (Recipe)
+
+### Build the GAM
 
@@
     step_ns(Runtime, deg_free = 2) %>%
-    step_ns(No_of_Votes, deg_free = 6)
+    step_ns(No_of_Votes, deg_free = 6) %>%
+    step_ns(IMDB_Rating, deg_free = 2)
 
@@
 ```{r}
-# Use the edf (round to integer) from above to create a recipe by adding step_ns() for the variables you want model with a non-linear relationship and do CV.
-Compare this model to one without any splines.
+# Build the GAM
 
@@
 
-cv_output <- fit_resamples( 
+cv_output_spline2 <- fit_resamples( 
   spline_wf, # workflow
@@
 
-cv_output %>% collect_metrics()
+```
+
+### Evaluation Metrics
+
+```{r}
+cv_output_spline2 %>% collect_metrics()
 
 ```
+
+### idk what this is for
 
@@
 
-# Variable Importance for GAM
+## GAM with Splines and LASSO
+
+### Build and Tune Model
 
@@
   set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
-  set_engine(engine = 'glmnet') %>% #note we are using a different engine
+  set_engine(engine = 'glmnet') %>% 
   set_mode('regression')
@@
 
-# Collect CV Metrics and Select Best Model
+### Collect CV Metrics and Select Best Model
 
@@
 
+### Fit Final GAM LASSO Model
+
+```{r}
 # Fit Final Model
 
-```{r}
+final_wf_gam_lasso <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow
 
-# Fit Final Model
-final_wf1 <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow
+final_fit_gam_lasso <- fit(final_wf_gam_lasso, data = imdb_clean)
 
-final_fit1 <- fit(final_wf1, data = imdb_clean)
-
-tidy(final_fit1)
+tidy(final_fit_gam_lasso)
 ```
@@
 
-final_fit1 %>% tidy() %>% filter(estimate != 0)
+final_fit_gam_lasso %>% tidy() %>% filter(estimate != 0)
 ```
 
-# Visualize Residuals
+### Evaluation Metrics
+
+```{r}
+gam_lasso_output <- fit_resamples( 
+  final_wf_gam_lasso, # workflow
+  resamples = data_cv10, # cv folds
+  metrics = metric_set(mae,rmse,rsq)
+)
+
+gam_lasso_output %>% collect_metrics()
+```
+
+## Compare GAMs
+
+```{r}
+gam1_output %>%
+    rmse(truth = Gross, estimate = .pred)
+
+cv_output_spline2 %>% collect_metrics()
+
+gam_lasso_output %>% collect_metrics()
+```
+
+The GAM created using TidyModels performs better than the recipe and LASSO GAMs.
+
+### Visualize Residuals for Final GAM
 
@@
 # Visualize Residuals
-lasso_mod_out1 <- new_mod %>%
+gam1_output <- new_mod %>%
     predict(new_data = imdb_clean) %>%
@@
 
-ggplot(lasso_mod_out1, aes(x = .pred, y = resid)) +
+ggplot(gam1_output, aes(x = .pred, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out1, aes(x = Runtime, y = resid)) +
+ggplot(gam1_output, aes(x = Runtime, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out1, aes(x = IMDB_Rating, y = resid)) +
+ggplot(gam1_output, aes(x = IMDB_Rating, y = resid)) +
     geom_point() +
@@
 
-ggplot(lasso_mod_out1, aes(x = No_of_Votes, y = resid)) +
+ggplot(gam1_output, aes(x = No_of_Votes, y = resid)) +
     geom_point() +
@@
 
-# Comparing Model Performance
+There does not appear to be any significant bias after analyzing the residuals.
+
+## Compare All Linear Regression Model Performance
 
@@
 ```{r}
-new_modcv %>% collect_metrics() #GAM
+gam1_output %>%
+    rmse(truth = Gross, estimate = .pred) #GAM
 ```
+
+The GAM with Splines obtained using TidyModels performs the best with the lowest RMSE value (1.3 compared to 1.4 for the others).
 
@@
 
+imdb_hc_full <- imdb_clean %>%
+  select(Gross, Budget)
+
 # Summary statistics for the variables
@@
 dist_mat_scaled <- dist(scale(imdb_hc_sub))
+
+dist_mat_full <- dist(scale(imdb_hc_full))
 ```
@@
 imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")
+imdb_full_avg <- hclust(dist_mat_full, method = "average")
 
@@
     mutate(
-        hclust_height = factor(cutree(imdb_hc_avg, h = 1.25)), # Cut at height (h) 3
-        hclust_num = factor(cutree(imdb_hc_avg, k = 5)) # Cut into 6 clusters (k)
+        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
     )
 
-plot(imdb_hc_avg, labels = imdb_clean$hclust_height)
 ```
+
+```{r}
+ggplot(imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+```

### 2022-12-08 Draft_Final_Code.Rmd
Organized RF Code

@@
 
-# Bagging and Random Forests
+# Classification Models
+
+## Create New Dataset for Classification
 
@@
 ```
+
+## Random Forests Model
+
+### Model Spec, Recipe, and Workflow
 
@@
 
+### Fit Models with Various Values for mtry
+
 ```{r}
@@
 ```
+
+### Obtain OOB Predictions and Evaluation Metrics
 
@@
 
-### Evaluating the Forest
+### Evaluating Selected Model - Confusion Matrix
 
@@
 ### Variable Importance
+
+#### Impurity
 
@@
 ```
+
+#### Permuation
 
@@
 ```
+
+### Violin Graphs
+
 ```{r}
@@
 
-# Logistic Regression
+## Logistic Regression
 

### 2022-12-08 Draft_Final_Code.Rmd
Finished Code Through Classification

@@
 gam_mod1 <- fit(gam_spec,
-    Gross ~ s(Runtime) + s(IMDB_Rating) + Meta_score + s(No_of_Votes) + Genre_1,
+    Gross ~ s(Runtime, k = 20) + s(IMDB_Rating) + Meta_score + s(No_of_Votes) + Genre_1,
     data = imdb_clean 
@@
     step_naomit(Gross) %>%
-    step_ns(Runtime, deg_free = 2) %>%
-    step_ns(No_of_Votes, deg_free = 6) %>%
-    step_ns(IMDB_Rating, deg_free = 2)
+    step_ns(Runtime, deg_free = 19) %>%
+    step_ns(No_of_Votes, deg_free = 9) %>%
+    step_ns(IMDB_Rating, deg_free = 9)
 
@@
 cv_output_spline2 %>% collect_metrics()
-
-```
-
-### idk what this is for
-
-```{r}
-new_mod <- spline_wf %>%
-  fit(data = imdb_clean)
-
-new_mod %>%
-  tidy()
-
-new_mod %>% 
-  tidy() %>% 
-  arrange(desc(abs(statistic)))
-
-new_modcv <- fit_resamples(spline_wf, resamples = data_cv10, metrics = metric_set(mae, rmse, rsq))
-```
-
-## GAM with Splines and LASSO
-
-### Build and Tune Model
-
-```{r}
-# Lasso Model Spec with tune
-gam_lasso_spec_tune <- 
-  linear_reg() %>%
-  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
-  set_engine(engine = 'glmnet') %>% 
-  set_mode('regression')
-
-# Recipe with standardization (!) --> just include all these always
-data_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
-                   No_of_Votes + Genre_1, data = imdb_clean) %>%
-    step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
-    step_novel(all_nominal_predictors()) %>% # important if you have rare categorical variables 
-    step_normalize(all_numeric_predictors()) %>%  # super important standardization step for LASSO
-    step_dummy(all_nominal_predictors()) %>%  # creates indicator variables for categorical variables
-    step_naomit(Gross)
-
-# Workflow (Recipe + Model)
-lasso_wf_tune1 <- workflow() %>% 
-  add_recipe(data_rec) %>%
-  add_model(gam_lasso_spec_tune)
-
-# Tune Model (trying a variety of values of Lambda penalty)
-penalty_grid <- grid_regular(
-  penalty(range = c(-3, 1)),
-  levels = 30)
-
-tune_res1 <- tune_grid( # new function for tuning parameters
-  lasso_wf_tune1, # workflow
-  resamples = data_cv10, # cv folds
-  metrics = metric_set(rmse, mae),
-  grid = penalty_grid # penalty grid defined above
-)
-
-# Visualize Model Evaluation Metrics from Tuning
-autoplot(tune_res1) + theme_classic()
-```
-
-### Collect CV Metrics and Select Best Model
-
-```{r}
-
-# Summarize Model Evaluation Metrics (CV)
-collect_metrics(tune_res) %>%
-  filter(.metric == 'rmse') %>% # or choose mae
-  select(penalty, rmse = mean)
-
-best_penalty1 <- select_best(tune_res1, metric = 'rmse') # choose penalty value based on lowest mae or rmse
-```
-
-### Fit Final GAM LASSO Model
-
-```{r}
-# Fit Final Model
-
-final_wf_gam_lasso <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow
-
-final_fit_gam_lasso <- fit(final_wf_gam_lasso, data = imdb_clean)
-
-tidy(final_fit_gam_lasso)
-```
-
-```{r}
-# Final ("best") model predictors and coefficients
-
-final_fit_gam_lasso %>% tidy() %>% filter(estimate != 0)
-```
-
-### Evaluation Metrics
-
-```{r}
-gam_lasso_output <- fit_resamples( 
-  final_wf_gam_lasso, # workflow
-  resamples = data_cv10, # cv folds
-  metrics = metric_set(mae,rmse,rsq)
-)
-
-gam_lasso_output %>% collect_metrics()
 ```
@@
 cv_output_spline2 %>% collect_metrics()
-
-gam_lasso_output %>% collect_metrics()
 ```
 
-The GAM created using TidyModels performs better than the recipe and LASSO GAMs.
+The GAM created using TidyModels performs better than the recipe and GAMs. Likely has to do with the degrees of freedom of the splines.
 
@@
 
-### Obtain OOB Predictions and Evaluation Metrics
+### Obtain OOB Predictions and Evaluation Metrics to Choose mtry Value
 
@@
 
+### Model Spec, Recipe, and Workflow
+
 ```{r}
@@
     add_model(logistic_spec)
+```
+
+### Fit Model
+
+```{r}
 
@@
 
+### Adds Variable for Odds Ratio
+
 ```{r}
@@
 ```
-
-*Ask Bryan about relevel factor... do we need it?*
 
@@
 
-# Recipes and Workflows
+# Cross Validation and Evaluation Metrics
 
 ```{r}
-full_log_wf <- workflow() %>%
-  add_recipe(logistic_rec) %>%
-  add_model(logistic_spec)
-
-log_model <- fit(full_log_wf, data = imdb_clean_class)
-
-log_modelcv <- fit_resamples(full_log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))
+log_modelcv <- fit_resamples(log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))
 
@@
 
+### Picking Threshold
+
+#### Boxplots
+
 ```{r}
-# Soft Predictions on Training Data
 final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)
@@
 ```
+
+#### ROC Curve
 
@@
 
+#### J Index vs. Threshold
+
 ```{r}
-# thresholds in terms of reference level
+# Thresholds in terms of reference level
 threshold_output <- final_output %>%
@@
 
-# J-index v. threshold for no flop
+# J-index v. Threshold for no flop
 threshold_output %>%
@@
 
+#### J Index vs. Distance
+
 ```{r}
@@
 ```{r}
-# Distance v. threshold for not_spam
+# Distance vs. Threshold
 
@@
 
+### Obtain Evaluation Metrics
+
 ```{r}
@@
 
+### Predictions
+
 ```{r}
@@
 
-```{r}
-predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
-                                        Genre_1 = "Drama"), type = "class"
-)
-```
-
-*Must manually calculate hard prediction*
+We manually performed the hard predictions.
 

### 2022-12-09 Draft_Final_Code.Rmd
More clustering work

@@
   cSplit("Genre", sep = ",", direction = "wide") %>%
-  mutate(Gross = log(Revenue-Budget)) %>%
-  select(-...15)
+  mutate(Gross = log(Revenue-Budget))
 
@@
 
-### K-Means Clustering
+# Unsupervised Learning - Clustering
+
+## K-Means Clustering
+
+### Preliminary Visualizations
 
@@
 
+### Create Clusters
+
 ```{r}
-# Select just the bill length and depth variables
 imdb_sub <- imdb_clean %>%
@@
 
-# Run k-means for k = centers = 3
 set.seed(253)
-kclust_k10 <- kmeans(scale(imdb_sub), centers = 10)
-
-# Display the cluter assignments
-kclust_k10$cluster
-
-# Add a variable (kclust_3) to the original dataset 
-# containing the cluster assignments
-imdb_clean <- imdb_clean %>%
-    mutate(kclust_10 = factor(kclust_k10$cluster))
 ```
 
-```{r}
-# Visualize the cluster assignments on the original scatterplot
-imdb_clean %>%
-  ggplot(aes(x = Budget, y = Runtime, color = kclust_10)) +
-    geom_point() + theme_classic()
-```
+### Determine Number of Clusters
 
@@
 
+### Select k = 8 Clusters
+
 ```{r}
@@
 
-# Display the cluter assignments
-kclust_k8$cluster
+kclust_k8$cluster   # Display cluster assignments
 
-# Add a variable (kclust_3) to the original dataset 
-# containing the cluster assignments
 imdb_clean <- imdb_clean %>%
@@
 ```
+
+### Visualize Cluster Assignments
 
@@
 
-*Pick either k = 8 or k = 10 --> there are 7 genres with larger n and 13 total genres.
-Film noir is fancy way of saying crime drama (ex.
-Knives Out).
-One thing to note is a significant number of movies have Genre_2 listed as Family Mystery and Horror (and many have one of the main genres listed as genre 2 as well).
-What is a good way to summarize both Genre 1 and 2?*
+### Interpreting Clusters
+
+#### Exploring Genre Breakdown
 
@@
   count(Genre_2)
+
+imdb_clean %>%
+  count(New_Genre)
 ```
 
-## Interpreting the Clusters
-
 ```{r}
-imdb_clean %>%
-  group_by(kclust_10) %>%
-  summarize(across(c(Gross, Budget), mean))
+# Genres vs Cluster
 
@@
   count(kclust_8)
+```
+
+```{r}
+imdb_clean %>%
+  ggplot(aes(x = kclust_8, fill = Genre_1)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+imdb_clean %>%
+  ggplot(aes(x = kclust_8, fill = Genre_2)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+imdb_clean %>%
+  ggplot(aes(x = kclust_8, fill = New_Genre)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
 ```

### 2022-12-09 Draft_Final_Code.Rmd
Complete Draft of Final Code

@@
 
-### Model Spec, Recipes, and Workflows for Linear Regression Model
+### Model Spec, Recipes, and Workflows
 
@@
 
-## Perform LASSO for Subset Selection
+## Perform LASSO for Subset Selection (Regression Model)
+
+### Model Spec, Recipes, and Workflow
 
@@
   add_model(lm_lasso_spec_tune) 
+```
+
+### Tune Model and Cross Validation
+
+```{r}
 
@@
 
-### Obtain Evaluation Metrics for Full Model
+### Obtain Evaluation Metrics for Lasso Model
 
@@
 
-### Evaluation Metrics
+### Obtain Evaluation Metrics for GAM1
 
@@
 
-### Evaluation Metrics
+### Obtain Evaluation Metrics for GAM2
 
@@
 
-### Visualize Residuals for Final GAM
+### Visualize Residuals for Final GAM (GAM1)
 
@@
 
-## Compare All Linear Regression Model Performance
+## Compare All Regression Model Performance
 
@@
 
-### Adds Variable for Odds Ratio
+### Add Variable for Odds Ratio
 
@@
 
+### Cross Validation and Evaluation Metrics
+
 ```{r}
@@
 ```
-
-# Cross Validation and Evaluation Metrics
 
@@
 
-### Obtain Evaluation Metrics
+### Obtain Evaluation Metrics for Logistic Regression
 
@@
 ```{r}
+
+# Count of Movies per Genre (Primary Genre)
 imdb_clean %>%
@@
 
+# Count of Movies per Genre (Secondary Genre)
 imdb_clean %>%
@@
 
+# Count of Movies per Genre (Overall Genre)
 imdb_clean %>%
@@
 
+# How many of each Genre 1 in each cluster
 imdb_clean %>%
@@
 
+# How many of each Genre 2 in each cluster
 imdb_clean %>%
@@
 
+# How many movies in each cluster
 imdb_clean%>%
@@
 
+#### Visualizations of Genres in Each Cluster
+
 ```{r}
+
+# Genre 1
 imdb_clean %>%
@@
 
+# Genre 2
 imdb_clean %>%
@@
 
+# Overall Genre
 imdb_clean %>%
@@
 
-### Hierarchial Clustering
+## Hierarchial Clustering
+
+### Set up Clustering and Distance Matrix
 
 ```{r}
-# Random subsample of 50 penguins
+# Random subsample of 25 Movies
 set.seed(253)
+
 imdb_hc <- imdb_clean %>%
@@
 # Compute a distance matrix on the scaled data
-dist_mat_scaled <- dist(scale(imdb_hc_sub))
+dist_mat_scaled <- dist(scale(imdb_hc_sub))     # Subset Distance Matrix
 
-dist_mat_full <- dist(scale(imdb_hc_full))
+dist_mat_full <- dist(scale(imdb_hc_full))      # Full Data Distance Matrix
 ```
 
+### Create Clusters
+
 ```{r}
-imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")
-imdb_full_avg <- hclust(dist_mat_full, method = "average")
+imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
+imdb_full_avg <- hclust(dist_mat_full, method = "average")    # Full Data
 
-# Plot dendrogram
+```
+
+### Visualize Dendrograms
+
+```{r}
+# Plot dendrogram on Subset
 plot(imdb_hc_avg)
@@
 ```{r}
+# Adding Genre Labels
 
@@
 plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2))
+
+plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3))
+
+plot(imdb_hc_avg, labels = paste(imdb_hc$New_Genre))
 ```
+
+### Cutting the Tree
 
@@
     )
+```
 
-```
+### Visualizing Genres in Final Clusters (Full Data)
 
@@
     theme_classic()
+
+ggplot(imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
+    geom_point() +
+    theme_classic()
 ```

### 2022-12-10 ClusteringModel.Rmd
checked some things

@@
 imdb_hc_sub <- imdb_hc %>%
-    select(Gross, Budget)
+    select(Budget, Runtime)
 
@@
 ```
+
+```{r}
+# Random subsample of 25 Movies
+set.seed(253)
+
+imdb_hc <- imdb_clean %>%
+    slice_sample(n = 25)
+
+# Select the variables to be used in clustering
+imdb_hc_sub <- imdb_hc %>%
+    select(Gross, Budget)
+
+imdb_hc_full1 <- imdb_clean %>%
+  select(Gross, Budget)
+
+imdb_hc_full2 <- imdb_clean %>%
+  select(Budget, Runtime)
+
+# Summary statistics for the variables
+summary(imdb_hc_sub)
+
+# Compute a distance matrix on the scaled data
+dist_mat_scaled <- dist(scale(imdb_hc_sub))     # Subset Distance Matrix
+
+dist_mat_full1 <- dist(scale(imdb_hc_full1))      # Full Data Distance Matrix
+dist_mat_full2 <- dist(scale(imdb_hc_full2))      # Full Data Distance Matrix
+```
+
+### Create Clusters
+
+```{r}
+imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
+imdb_full_avg1 <- hclust(dist_mat_full1, method = "average")    # Full Data
+imdb_full_avg2 <- hclust(dist_mat_full2, method = "average")    # Full Data
+```
+
+### Cutting the Tree
+
+```{r}
+one_imdb_clean <- imdb_clean %>%
+    mutate(
+        hclust_num = factor(cutree(imdb_full_avg1, k = 3)) # Cut into 6 clusters (k)
+    )
+
+two_imdb_clean <- imdb_clean %>%
+    mutate(
+        hclust_num = factor(cutree(imdb_full_avg2, k = 2)) # Cut into 6 clusters (k)
+    )
+```
+
+### Visualizing Genres in Final Clusters (Full Data)
+
+```{r}
+ggplot(one_imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+ggplot(two_imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+ggplot(one_imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+
+ggplot(two_imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
+    geom_bar(position = "fill") +
+    labs(x = "Cluster") + 
+    theme_classic()
+```

### 2022-12-10 Draft_Final_Code.Rmd
checked some things

@@
 ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
-  geom_point() + theme_classic()
+  geom_point() + 
+  labs(x = "Budget", y = "Log(Gross)") +
+  theme_classic()
 
@@
     theme_classic()
+
+imdb_clean %>%
+  count(hclust_num)
 ```

### 2022-12-10 Draft_Final_Code.Rmd
Fixed missing cases

--- 2022-12-09 Draft_Final_Code.Rmd
@@
 ```{r}
-imdb_clean_class <- imdb_clean %>%
+imdb_class <- imdb_top_1000 %>%
+  cSplit("Genre", sep = ",", direction = "wide") %>%
+  mutate(Gross = Revenue-Budget)
+
+runtime_clean <- imdb_top_1000$Runtime %>%
+  str_replace(" min", "") %>%
+  as.numeric()
+
+imdb_class$Runtime <- runtime_clean
+
+imdb_class <- imdb_class %>%
+  drop_na(Gross, Budget)
+
+imdb_clean_class <- imdb_class %>%
   mutate(success_ratio = Revenue/Budget) %>%
@@
 final_output %>%
-    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
     log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
@@
 final_output %>%
-  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
   conf_mat(truth = flop, estimate = .pred_class)
@@
 ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
-  geom_point() + theme_classic()
+  geom_point() + 
+  labs(x = "Budget in USD", 
+       y = "Gross Profit in USD (Log Scale)", 
+       title = "Preliminary Visualizations") +
+  theme_classic()
 
@@
 imdb_hc <- imdb_clean %>%
-    slice_sample(n = 25)
+  slice_sample(n = 25) %>%
+  filter(Budget != 0)
 
@@
 imdb_hc_full <- imdb_clean %>%
-  select(Gross, Budget)
+  select(Gross, Budget) %>%
+  filter(Budget != 0)
 
@@
 ```{r}
-imdb_clean <- imdb_clean %>%
+imdb_clean_clust <- imdb_clean %>%
+  filter(Budget != 0) %>%
     mutate(
@@
 ```{r}
-ggplot(imdb_clean, aes(x = hclust_num, fill = Genre_1)) +
+ggplot(imdb_clean_clust, aes(x = hclust_num, fill = Genre_1)) +
     geom_bar(position = "fill") +
@@
 
-ggplot(imdb_clean, aes(x = hclust_num, fill = New_Genre)) +
+ggplot(imdb_clean_clust, aes(x = hclust_num, fill = New_Genre)) +
     geom_bar(position = "fill") +
@@
 
-ggplot(imdb_clean, aes(x = Budget, y = Gross, color = hclust_num)) +
+ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num)) +
     geom_point() +
     theme_classic()
+
+imdb_clean_clust %>%
+  count(hclust_num)
+
+imdb_clean_clust %>%
+  count(Genre_1)
 ```

### 2022-12-11 Draft_Final_Code.Rmd
Worked on Plots

@@
 # Fit Models
-set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
+set.seed(123)
 data_fit_mtry3 <- fit(data_wf_mtry3, data = imdb_clean_class)
@@
 
-#### J Index vs. Distance
-
 ```{r}
@@
 ```
+
+#### Distance vs. Threshold
 
@@
 
-### Obtain Evaluation Metrics for Logistic Regression
+### Obtain Evaluation Metrics for Logistic Regression Model with Thresholds
 
 ```{r}
+# To determine final threshold
+
 log_metrics <- metric_set(accuracy,sens,yardstick::spec)
@@
 final_output %>%
-    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .78)) %>%
     log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
@@
 final_output %>%
-  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
+    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .71)) %>%
+    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')
+
+final_output %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .78)) %>%
+  conf_mat(truth = flop, estimate = .pred_class)
+
+final_output %>%
+  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .71)) %>%
   conf_mat(truth = flop, estimate = .pred_class)
@@
 
-We manually performed the hard predictions.
+We manually performed the hard predictions with threshold = .78.
 
@@
   select(Gross, Budget) %>%
-  filter(Budget != 0)
+  filter(Budget > 1)
 
@@
 
-### Create Clusters
+### Perform Fusing Process
 
@@
 imdb_full_avg <- hclust(dist_mat_full, method = "average")    # Full Data
-
 ```
@@
 
-plot(imdb_hc_avg, labels = imdb_hc$Genre_1)
+plot(imdb_hc_avg, labels = imdb_hc$Genre_1, main = "Movie Clusters", xlab = NULL)
 
@@
 
-plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3))
+plot(imdb_hc_avg, 
+     main = "Visualizing Movie Clusters",
+     labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3), 
+     hang = -1, 
+     cex = 1)
 
@@
 
-### Cutting the Tree
+### Cutting the Tree (Choosing k)
 
@@
 imdb_clean_clust <- imdb_clean %>%
-  filter(Budget != 0) %>%
+  filter(Budget > 1) %>%
     mutate(
-        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
+        hclust_num2 = factor(cutree(imdb_full_avg, k = 2)), # Cut into 2 clusters (k)
+        hclust_num4 = factor(cutree(imdb_full_avg, k = 4)), # Cut into 4 clusters (k)
+        hclust_num8 = factor(cutree(imdb_full_avg, k = 8)) # Cut into 8 clusters (k)
     )
+```
+
+```{r}
+ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
+  geom_bar(position = "fill") +
+  labs(x = "Cluster", 
+       y = "Proportion of Cluster", 
+       title = "Selecting Number of Clusters (k)") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
+
+ggplot(imdb_clean_clust, aes(x = hclust_num4, fill = Genre_1)) +
+  geom_bar(position = "fill") +
+  labs(x = "Cluster", 
+       y = "Proportion of Cluster", 
+       title = "Selecting Number of Clusters (k)") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
+
+ggplot(imdb_clean_clust, aes(x = hclust_num8, fill = Genre_1)) +
+  geom_bar(position = "fill") +
+  labs(x = "Cluster", 
+       y = "Proportion of Cluster", 
+       title = "Selecting Number of Clusters (k)") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
 ```
@@
 ```{r}
-ggplot(imdb_clean_clust, aes(x = hclust_num, fill = Genre_1)) +
+ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
     geom_bar(position = "fill") +
@@
 
-ggplot(imdb_clean_clust, aes(x = hclust_num, fill = New_Genre)) +
+ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = New_Genre)) +
     geom_bar(position = "fill") +
@@
 
-ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num)) +
+ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num2)) +
   geom_point() +
-    theme_classic()
+  labs(x = "Budget in USD", 
+       y = "Gross Profit in USD (Log Scale)", 
+       title = "Visualizing Clusters: Gross Profit vs. Budget") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
+
+ggplot(imdb_clean_clust, aes(x = hclust_num2, y = Budget)) +
+  geom_boxplot() +
+  labs(x = "Cluster", 
+       y = "Budget in USD", 
+       title = "Visualizing Clusters: Budget") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
+
+ggplot(imdb_clean_clust, aes(x = hclust_num2, y = Gross)) +
+  geom_boxplot() +
+  labs(x = "Cluster", 
+       y = "Gross Profit in USD (Log Scale)", 
+       title = "Visualizing Clusters: Gross Profit") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
 
 imdb_clean_clust %>%
-  count(hclust_num)
+  count(hclust_num2)
 
 imdb_clean_clust %>%
-  count(Genre_1)
+  group_by(hclust_num2) %>%
+  summarize(mean(Gross), sd(Gross), min(Gross), max(Gross),
+            mean((Budget/100000)), sd((Budget/100000)), min((Budget/100000)), max((Budget/100000)))
 ```

### 2022-12-11 Draft_Final_Code.Rmd
Unsupervised Code Done

@@
   geom_bar(position = "fill") +
-    labs(x = "Cluster") + 
-    theme_classic()
+  labs(x = "Cluster", 
+       y = "Proportion of Cluster", 
+       title = "Selecting Number of Clusters (k)", 
+       fill = "Genre 1") + 
+  theme_classic() + 
+  theme(plot.title = element_text(size = 20, face = "bold"))
 
@@
        y = "Gross Profit in USD (Log Scale)", 
-       title = "Visualizing Clusters: Gross Profit vs. Budget") + 
+       title = "Visualizing Clusters: Gross Profit vs. Budget",
+       color = "Clusters") + 
   theme_classic() + 

### 2022-12-11 Draft_Final_Code.Rmd
Fixed degrees of freedom

@@
     step_naomit(Gross) %>%
-    step_ns(Runtime, deg_free = 19) %>%
-    step_ns(No_of_Votes, deg_free = 9) %>%
-    step_ns(IMDB_Rating, deg_free = 9)
+    step_ns(Runtime, deg_free = 20) %>%
+    step_ns(No_of_Votes, deg_free = 10) %>%
+    step_ns(IMDB_Rating, deg_free = 10)
 

### 2022-12-11 Draft_Final_Code.Rmd
Made the Residual Graphs nice

@@
     geom_hline(yintercept = 0, color = "red") + 
+    labs(x = "Prediction",
+         y = "Residuals", 
+         title = "Residuals vs. Predictions") +
     theme_classic()
@@
     geom_hline(yintercept = 0, color = "red")  + 
+    labs(x = "Runtime",
+         y = "Residuals", 
+         title = "Residuals vs. Runtime") +
     theme_classic()
@@
     geom_hline(yintercept = 0, color = "red")  + 
+    labs(x = "IMDB Rating",
+         y = "Residuals", 
+         title = "Residuals vs. IMDB Rating") +
     theme_classic()
@@
     geom_hline(yintercept = 0, color = "red")  + 
+    labs(x = "Number of Votes",
+         y = "Residuals", 
+         title = "Residuals vs. Number of Votes") +
     theme_classic()

### 2022-12-11 Draft_Final_Code.Rmd
Added titles to plots

@@
 
-gam_mod1 %>% pluck('fit') %>% plot()
+gam_mod1 %>% pluck('fit') %>% plot(main = "Non-Linear Visualizations")
 ```
@@
 
-ggplot(imdb_clean, aes(x = Budget, y = Gross)) + 
+imdb_clean %>%
+  filter(Budget > 1) %>% 
+  ggplot(aes(x = Budget, y = Gross)) + 
   geom_point() + 

### 2022-12-12 Project_Final_Code.Rmd
Fixed GAM

--- 2022-12-11 Draft_Final_Code.Rmd
@@
 ---
-title: "Final Project Code ALL"
+title: "Final Project Code"
 author: "Emily, Julian, Jacob, and Aristo"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE, tidy = TRUE)
 ```
@@
     rmse(truth = Gross, estimate = .pred)
-
-gam1_output %>%
-    rsq(truth = Gross, estimate = .pred)
 ```
@@
 # Visualize Residuals
-gam1_output <- new_mod %>%
+cv_output_spline2 <- new_mod %>%
     predict(new_data = imdb_clean) %>%
@@
 
-ggplot(gam1_output, aes(x = .pred, y = resid)) +
+ggplot(cv_output_spline2, aes(x = .pred, y = resid)) +
     geom_point() +
@@
 
-ggplot(gam1_output, aes(x = Runtime, y = resid)) +
+ggplot(cv_output_spline2, aes(x = Runtime, y = resid)) +
     geom_point() +
@@
 
-ggplot(gam1_output, aes(x = IMDB_Rating, y = resid)) +
+ggplot(cv_output_spline2, aes(x = IMDB_Rating, y = resid)) +
     geom_point() +
@@
 
-ggplot(gam1_output, aes(x = No_of_Votes, y = resid)) +
+ggplot(cv_output_spline2, aes(x = No_of_Votes, y = resid)) +
     geom_point() +
@@
 ```{r}
-gam1_output %>%
+cv_output_spline2 %>%
     rmse(truth = Gross, estimate = .pred) #GAM

### 2022-12-12 ClusteringModel.Rmd
Final Code

@@
 imdb_hc_full2 <- imdb_clean %>%
-  select(Budget, Runtime)
+  select(Budget, Revenue)
 
@@
     mutate(
-        hclust_num = factor(cutree(imdb_full_avg2, k = 2)) # Cut into 6 clusters (k)
+        hclust_num = factor(cutree(imdb_full_avg2, k = 3)) # Cut into 6 clusters (k)
     )
@@
     theme_classic()
+
+one_imdb_clean %>%
+  count(hclust_num)
+
+two_imdb_clean %>%
+  count(hclust_num)
 ```

### 2022-12-12 Project_Final_Code.Rmd
Final Code

--- 2022-12-11 Draft_Final_Code.Rmd
@@
 ```{r}
+# All predictors included
+
 full_lm_model <- fit(full_lm_wf, data = imdb_clean)
@@
 ```{r}
+# Cross Validation Performed (10 folds)
+
 full_lm_modelcv <- fit_resamples(full_lm_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))
@@
 ```{r}
-
-# Tune Model (trying a variety of values of Lambda penalty)
+# Tune Model (to select best Lambda penalty) -- via Cross Validation
 
@@
 ```{r}
-# Fit Final Model
+# Fit Final Model -- Subset of Variables
 
@@
 
+tidy(final_fit)
+
+# Final ("best") model predictors and coefficients
+
+final_fit %>% tidy() %>% filter(estimate != 0)
+```
+
+### Obtain Evaluation Metrics for Lasso Model
+
+```{r}
+# Cross Validation Performed (10 folds)
+
 lasso_fit <- fit_resamples(final_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))
 
-tidy(final_fit)
-
-# Final ("best") model predictors and coefficients
-
-final_fit %>% tidy() %>% filter(estimate != 0)
-```
-
-### Obtain Evaluation Metrics for Lasso Model
-
-```{r}
 lasso_fit %>%
@@
 
-### Visualization for Non-Linear Functions
+### Visualizations for Non-Linear Functions
 
@@
     rsq(truth = Gross, estimate = .pred)
+
+# Note: Unable to obtain std error for eval metrics bc can't perform cross validation w/ TidyModels
 ```
@@
     step_ns(IMDB_Rating, deg_free = 10)
+# Chose degrees of freedom to attempt to match # of knots from TidyModels
+# May not be an exact match, but it's close
 
@@
     add_recipe(spline_rec)
+
+GAM2_fit <- fit(spline_wf, data = imdb_clean)
+
+tidy(GAM2_fit)
+```
+
+### Obtain Evaluation Metrics for GAM2
+
+```{r}
+# Cross Validation Performed (10 folds)
 
@@
 
-```
-
-### Obtain Evaluation Metrics for GAM2
-
-```{r}
 cv_output_spline2 %>% collect_metrics()
@@
 ```{r}
+# Compare RMSE values --> pick model with lower RMSE
+
 gam1_output %>%
@@
 
-The GAM created using TidyModels performs better than the recipe and GAMs. Likely has to do with the degrees of freedom of the splines.
+The GAM created using TidyModels performs better than the recipe GAM based on RMSE.
+Likely has to do with the degrees of freedom of the splines.
+However, it is worth noting that we were unable to perform cross validation on the TidyModels GAM.
 
@@
 ```{r}
-
-# Visualize Residuals
-gam1_output <- new_mod %>%
-    predict(new_data = imdb_clean) %>%
-    bind_cols(imdb_clean) %>%
-    mutate(resid = Gross - .pred)
+# Visualize Residuals for Final GAM (TidyModels GAM)
 
@@
 There does not appear to be any significant bias after analyzing the residuals.
+The trendline for Residuals vs.
+Runtime trends up at the end points since there are only a few cases with very short and very long runtimes.
 
@@
 ```{r}
-full_lm_modelcv %>% collect_metrics() #OLS
-```
-
-```{r}
-lasso_fit %>% collect_metrics() #LASSO
-```
-
-```{r}
+# Eval Metrics from CV
+
+full_lm_modelcv %>% collect_metrics() # OLS
+```
+
+```{r}
+# Eval Metrics from CV
+
+lasso_fit %>% collect_metrics() # LASSO
+```
+
+```{r}
+# Eval Metrics from CV
+
 gam1_output %>%
-    rmse(truth = Gross, estimate = .pred) #GAM
-```
-
-The GAM with Splines obtained using TidyModels performs the best with the lowest RMSE value (1.3 compared to 1.4 for the others).
+    rmse(truth = Gross, estimate = .pred) # GAM
+```
+
+The GAM with Splines obtained using TidyModels performs the best with the lowest RMSE value (approx. 1.3 compared to approx. 1.4 for the others).
 
@@
 ```{r}
+# Remove log transformation from Gross
+
 imdb_class <- imdb_top_1000 %>%
@@
   mutate(flop = as.factor(ifelse(success_ratio > 2, 'FALSE', 'TRUE'))) %>%
-  drop_na(flop, No_of_Votes,Runtime, IMDB_Rating,Meta_score,Genre_1)
+  drop_na(flop, No_of_Votes, Runtime, IMDB_Rating, Meta_score, Genre_1)
 ```
@@
 
-# Create Workflows
+# Create Workflows to Test Various Values for mtry
+
  data_wf_mtry3 <- workflow() %>%
@@
 ```{r}
-# Fit Models
+# Fit Models (for each mtry value)
+
 set.seed(123)
@@
 # Custom Function to get OOB predictions, true observed outcomes and add a user-provided model label
+
 rf_OOB_output <- function(fit_model, model_label, truth){
@@
 
+# OOB Accuracy for Each mtry Value
+
 data_rf_OOB_output %>% 
@@
     accuracy(truth = flop, estimate = .pred_class)
+
+data_rf_OOB_output %>% 
+    group_by(model) %>%
+    sensitivity(truth = flop, estimate = .pred_class)
+# mtry = 3 and 4 tied for best sensitivity
+
+# Accuracy vs. mtry Plot
 
@@
   theme_classic()
-```
-
-### Evaluating Selected Model - Confusion Matrix
-
-```{r}
+# Select mtry = 4 based on accuracy
+```
+
+### Evaluating Selected Model - Confusion Matrix and Evaluation Metrics
+
+```{r}
+# Confusion Matrix
+
 rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
     conf_mat(truth = flop, estimate= .pred_class)
+
+# Sensitivity, Specificity, and Accuracy
+
+rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
+  sensitivity(truth = flop, estimate= .pred_class)
+
+rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
+  specificity(truth = flop, estimate= .pred_class)
+
+rf_OOB_output(data_fit_mtry4,4, imdb_clean_class %>% pull(flop)) %>%
+  accuracy(truth = flop, estimate= .pred_class)
 ```
@@
 ```{r}
-
 # Fit Model
+
 log_fit <- fit(log_wf, data = imdb_clean_class)
@@
 # Creation of CV Folds
+
 data_cv10_class <- vfold_cv(imdb_clean_class, v = 10)
@@
 ```{r}
+# Cross Validation Performed (10 folds)
+
 log_modelcv <- fit_resamples(log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))
@@
 # Thresholds in terms of reference level
+
 threshold_output <- final_output %>%
@@
 # J-index v. Threshold for no flop
+
 threshold_output %>%
@@
 
+# Compare Eval Metrics
+
 final_output %>%
@@
 
+# Compare Confusion Matrices
+
 final_output %>%
@@
 
+We chose the threshold of 0.78 for our final model because we are prioritizing sensitivity over accuracy and specificity.
+
 ### Predictions
@@
 
-We manually performed the hard predictions with threshold = .78.
+We manually performed the hard predictions with threshold = .78. Since .pred_FALSE = 0.56 which is lower than our threshold of 0.78, we would predict this example movie would flop (flop = TRUE).
 
@@
 
-### Create Clusters
+### Feature Selection
 
@@
 imdb_sub <- imdb_clean %>%
-    select(Budget, Runtime)
+    select(Budget, Gross)
 
@@
 imdb_clean %>%
-  ggplot(aes(x = Budget, y = Runtime, color = kclust_8)) +
+  ggplot(aes(x = Budget, y = Gross, color = kclust_8)) +
     geom_point() + theme_classic()
@@
 
-## Hierarchial Clustering
+## Hierarchical Clustering
 

### 2022-12-12 Project_Final_Code.Rmd
FINAL code for project

@@
 ---
-title: "Final Project Code"
+title: "Code Appendix"
 author: "Emily, Julian, Jacob, and Aristo"
-date: '2022-11-20'
+date: '2022-12-12'
 output: 
